---
title: "Dionex_COMPASS_TEMPEST"
author: "Stephanie J. Wilson"
date: '2023-06-09'
output: html_document
---
## Daily Set up 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## Load data.table package
library(data.table)
library(ggplot2)
library(dplyr)
library(data.table)
library(matrixStats)
library(gridExtra)
library(ggpubr)
library(grid)
library(stringr)
```


### Read in and Format the raw data - change wd & file names (Make sure files are UTF-8 encoded)
```{r}
setwd("S:/Biogeochemistry/People/Wilson (Steph)/Data/RAD7/July 2023 Tidal Survey/Survey Data/Dionex Files")

# SULFATE DATA: 

## Read in raw data file from Dionex - copied and saved as a txt
Sdat <- read.table("Flume_Tidal_Survey_202408_SO4.txt",sep='\t' , header=T, skip=3)
head(Sdat)

## Only keep the columns that we need 
Sdat <- Sdat[ ,c(2,5,7)] # dont need this here 
head(Sdat)

## Name the columns correctly 
colnames(Sdat) <- c( "Sample_ID", "SO4_ppm", "SO4_Area")
Sdat$Sample_ID <- as.factor(Sdat$Sample_ID)
Sdat$SO4_ppm <- as.numeric(Sdat$SO4_ppm)
Sdat$SO4_Area <- as.numeric(Sdat$SO4_Area)
Sdat <- as.data.frame(Sdat)
head(Sdat)

#Chloride data 
## Read in raw data file from Dionex - copied and saved as a txt
Cldat <- read.table("Flume_Tidal_Survey_202408_Cl.txt",sep='\t' , header=T, skip=3)
head(Cldat)

## Only keep the columns that we need 
Cldat <- Cldat[ ,c(2,5,7)]
head(Cldat)

## Name the columns correctly 
colnames(Cldat) <- c( "Sample_ID", "Cl_ppm", "Cl_Area")
Cldat$Sample_ID <- as.factor(Cldat$Sample_ID)
Cldat$Cl_ppm <- as.numeric(Cldat$Cl_ppm)
Cldat$Cl_Area <- as.numeric(Cldat$Cl_Area)
Cldat <- as.data.frame(Cldat)
head(Cldat) 


## Bring the data back together: 
all_dat <- merge(Sdat, Cldat, by="Sample_ID")
head(all_dat)

## Remove empty lines 
all_dat <- all_dat[!(is.na(all_dat$Sample_ID) | all_dat$Sample_ID==""), ]
head(all_dat)

all_dat <- droplevels(all_dat[!all_dat$Sample_ID == 'Lab Blank',])
head(all_dat)

all_dat[is.na(all_dat)] <- 0

```


## Pull out standards  - could do some checks here if we want
```{r}
stds <- all_dat[grepl("Standard", all_dat$Sample_ID),]
head(stds)

stds_chk_S <- stds %>%
	group_by(Sample_ID) %>%
	summarise(mean = mean(SO4_ppm), sd = sd(SO4_ppm))
stds_chk_S$cv <- (stds_chk_S$sd/stds_chk_S$mean)*100
stds_chk_S$flag <-  ifelse(stds_chk_S$cv <2, 'YES', 'NO, rerun')
head(stds_chk_S)

stds_chk_Cl <- stds %>%
	group_by(Sample_ID) %>%
	summarise(mean = mean(Cl_ppm), sd = sd(Cl_ppm))
stds_chk_Cl$cv <- (stds_chk_Cl$sd/stds_chk_Cl$mean)*100
stds_chk_Cl$flag <-  ifelse(stds_chk_Cl$cv <2, 'YES', 'NO, rerun')
head(stds_chk_Cl)

lmS <- lm(stds$SO4_Area ~ stds$SO4_ppm)
SO4_sum <- summary(lmS)
SO4_Slope <- SO4_sum$coefficients[2, 1] 
SO4_Int <- SO4_sum$coefficients[1, 1] 


lmCl <- lm(stds$Cl_Area ~ stds$Cl_ppm)
Cl_sum <- summary(lmCl)
Cl_Slope <- Cl_sum$coefficients[2, 1] 
Cl_Int <- Cl_sum$coefficients[1, 1] 

```


## Calculate mmol/L concentrations
```{r}
#remove standards from sample dataframe
sampledat <- all_dat[!grepl("Standard", all_dat$Sample_ID),]
head(sampledat)

# Constants needed for calculations: 
clmw <- 35.45     #molecular weight of Chloride: 35.45 
smw <- 32.06      #molecular weight of sulfur: 32.06


# Convert ppm to mmol/L
sampledat$SO4_mM <- (sampledat$SO4_ppm / smw)
sampledat$Cl_mM <- (sampledat$Cl_ppm / clmw)


# Calculate Salinity 
# calculated using the Knudsen equation 
# Salinity = 0.03 + 1.8050 * Chlorinity
# Ref: A Practical Handbook of Seawater Analysis by Strickland & Parsons (P. 11)
# =((1.807*Cl_ppm)+0.026)/1000
sampledat$salinity <- ((1.8070 * sampledat$Cl_ppm) + 0.026) / 1000


head(sampledat)
```


## Pull out dups and check with percent difference 
```{r}
#Show me the data that we have from the calculations 
head(sampledat)

#pull out any rows that have "dup" in the SampleID column
dups <- sampledat %>%  
  filter(str_detect(Sample_ID, "_dup"))      #have to change this to match data
head(dups)

#remove these from sample dataframe in a new dataframe
sampledat2 <- sampledat %>%  
  filter(!str_detect(Sample_ID, "_dup")) %>%  
  filter(!str_detect(Sample_ID, "_spk")) 
head(sampledat2)

#remove the dup from these IDs so we will have duplicate sample names
dups$Sample_ID<-gsub("_dup","",as.character(dups$Sample_ID))
dups <- dups[ ,-c(2:5)]
colnames(dups) <- c('Sample_ID', 'SO4_mM_dup', "Cl_mM_dup", "salinity_dup")
head(dups)

#put it back together with the old data set and look for duplicates 
QAdups <- merge(sampledat2, dups)
head(QAdups)

QAdups$SO4_dups_chk <- ((abs(QAdups$SO4_mM-QAdups$SO4_mM_dup))/((QAdups$SO4_mM+QAdups$SO4_mM_dup)/2))*100
QAdups$SO4_dups_flag <-  ifelse(QAdups$SO4_dups_chk <10, 'YES', 'NO, rerun')

QAdups$Cl_dups_chk <- ((abs(QAdups$Cl_mM-QAdups$Cl_mM_dup))/((QAdups$Cl_mM+QAdups$Cl_mM_dup)/2))*100
QAdups$Cl_dups_flag <-  ifelse(QAdups$Cl_dups_chk <10, 'YES', 'NO, rerun')

head(QAdups)

#plot dups output as a bar graph to easily check - want any over 10% to be red need to work on this 
Sdupsbar <- ggplot(data = QAdups, aes(x = Sample_ID, y = SO4_dups_chk, fill=SO4_dups_chk)) +
       geom_bar(stat = 'identity') + 
        scale_fill_gradient2(low='darkgreen', mid='darkgreen', high='darkgrey', space='Lab') + 
        theme_classic() + labs(x= "Sample ID", y="Difference Between SO4 Duplicates (%)") + 
        theme(legend.position="none") +  geom_hline(yintercept=10, linetype="dashed", 
                color = "black", size=1)


Cldupsbar <- ggplot(data = QAdups, aes(x = Sample_ID, y = Cl_dups_chk, fill=Cl_dups_chk)) +
       geom_bar(stat = 'identity') + 
        scale_fill_gradient2(low='darkgreen', mid='darkgreen', high='darkgrey', space='Lab') + 
        theme_classic() + labs(x= "Sample ID", y="Difference Between Cl Duplicates (%)") + 
        theme(legend.position="none") +  geom_hline(yintercept=10, linetype="dashed", 
                color = "black", size=1)

ggarrange(Sdupsbar, Cldupsbar,ncol=2, nrow=1)

#check for percent of no, reruns to see if it  would warrant reruns 
Perc_dups <- QAdups %>% 
  group_by(SO4_dups_flag) %>%
  summarise(S_no_rows = length(SO4_dups_flag)) 
Perc_dups1 <- QAdups %>% 
  group_by(Cl_dups_flag) %>%
  summarise(Cl_no_rows = length(Cl_dups_flag))
colnames(Perc_dups) <- c("Flag", "S_no_rows")
colnames(Perc_dups1) <- c("Flag", "Cl_no_rows")
Perc_dups2 <- cbind(Perc_dups, Perc_dups1)

Perc_dups2$Total <- length(QAdups$SO4_dups_flag)
Perc_dups2$S_Percent <- (Perc_dups2$S_no_rows / Perc_dups2$Total)*100
Perc_dups2$Cl_Percent <- (Perc_dups2$Cl_no_rows / Perc_dups2$Total)*100
head(Perc_dups2)


```


## Pull out dups and check with cv  
```{r}
#the cv 
# calculate the sd bewteen the two duplicates then divide by the mean and multiply by 100 

df2 <- as.data.frame(QAdups$SO4_mM)
df2$dups <- QAdups$SO4_mM_dup

df2$sds <- apply(df2,1,sd)

QAdups$SO4_dups_cv <- (df2$sds)/((QAdups$SO4_mM+QAdups$SO4_mM_dup)/2) * 100
QAdups$SO4_dups_cv_flag <-  ifelse(QAdups$SO4_dups_cv <11, 'YES', 'NO, rerun')

head(QAdups)

#plot dups output as a bar graph to easily check - want any over 10% to be red need to work on this 
Sdupsbar <- ggplot(data = QAdups, aes(x = Sample_ID, y = SO4_dups_cv, fill=SO4_dups_chk)) +
       geom_bar(stat = 'identity') + 
        scale_fill_gradient2(low='darkgreen', mid='darkgreen', high='darkgrey', space='Lab') + 
        theme_classic() + labs(x= "Sample ID", y="CV Between SO4 Duplicates (%)") + 
        theme(legend.position="none") +  geom_hline(yintercept=10, linetype="dashed", 
                color = "black", size=1)


Cldupsbar <- ggplot(data = QAdups, aes(x = Sample_ID, y = Cl_dups_chk, fill=Cl_dups_chk)) +
       geom_bar(stat = 'identity') + 
        scale_fill_gradient2(low='darkgreen', mid='darkgreen', high='darkgrey', space='Lab') + 
        theme_classic() + labs(x= "Sample ID", y="CV Between Cl Duplicates (%)") + 
        theme(legend.position="none") +  geom_hline(yintercept=10, linetype="dashed", 
                color = "black", size=1)

ggarrange(Sdupsbar, Cldupsbar,ncol=2, nrow=1)

#check for percent of no, reruns to see if it  would warrant reruns 
Perc_dups <- QAdups %>% 
  group_by(SO4_dups_flag) %>%
  summarise(S_no_rows = length(SO4_dups_flag)) 
Perc_dups1 <- QAdups %>% 
  group_by(Cl_dups_flag) %>%
  summarise(Cl_no_rows = length(Cl_dups_flag))
colnames(Perc_dups) <- c("Flag", "S_no_rows")
colnames(Perc_dups1) <- c("Flag", "Cl_no_rows")
Perc_dups2 <- cbind(Perc_dups, Perc_dups1)

Perc_dups2$Total <- length(QAdups$SO4_dups_flag)
Perc_dups2$S_Percent <- (Perc_dups2$S_no_rows / Perc_dups2$Total)*100
Perc_dups2$Cl_Percent <- (Perc_dups2$Cl_no_rows / Perc_dups2$Total)*100
head(Perc_dups2)


```


## Pull out spikes and check with dionex output conc. 
```{r}
#Show me the data that we have from the calculations 
head(sampledat)

#pull out any rows that have "spk" in the SampleID column
spks <- sampledat %>%  
  filter(str_detect(Sample_ID, "spk"))      #have to change this to match data
head(spks)

#remove the dup from these IDs so we will have duplicate sample names
spks$Sample_ID<-gsub("_spk","",as.character(spks$Sample_ID))
spks <- spks[ ,-c(2,3,4 ,5, 7,8)]
colnames(spks) <- c('Sample_ID', 'SO4_mM_spk')
head(spks)

#put it back together with the old data set and look for duplicates 
QAspks <- merge(sampledat, spks)
head(QAspks)

#now we need to calculate the spike concentration and calculate the spike recovery
spkconc <- (250/smw)    # in mM
spkvol <- 10             # in uL
spkvol <- spkvol/1000000 
#spike for these samples was 10uL of the 250mM standard
QAspks$SO4_spk_Conc <- (spkconc)*spkvol         # mmoles of SO4 
head(QAspks)

#need to determine dilution factors and initial amount of sample added
#if your samples are all the same dilution just use the first line 
#for Steph / COMPASS this depends on the site so... 
QAspks$Dilution <- 1
QAspks$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "FTS_"), 100, QAspks$Dilution)
QAspks$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "Aquifer"), 50, QAspks$Dilution)



#Set Sample volumes in uL 
QAspks$SampleVol <- 1
QAspks$SampleVol <-  ifelse(str_detect(QAspks$Sample_ID, "FTS_"), 1475, QAspks$SampleVol)
QAspks$SampleVol <-  ifelse(str_detect(QAspks$Sample_ID, "Aquifer"), 1501, QAspks$SampleVol)


#change sample volume to L 
QAspks$SampleVol <- QAspks$SampleVol/1000000
head(QAspks)

#gives us the total SO4 in the sample in mmoles
QAspks$SO4_Total_unspkd <- (QAspks$SO4_mM/QAspks$Dilution)*(QAspks$SampleVol) 

##total SO4 in spiked sample in mmoles
QAspks$SO4_Total_spkd <- (QAspks$SO4_mM_spk/QAspks$Dilution)*(QAspks$SampleVol+spkvol) 

QAspks$SO4_expctd_spkd <-  (QAspks$SO4_Total_unspkd + QAspks$SO4_spk_Conc)
QAspks$spk_recovery <-    (QAspks$SO4_Total_spkd/QAspks$SO4_expctd_spkd)*100
QAspks$SO4_spks_flag <-  ifelse(QAspks$spk_recovery <=120 & QAspks$spk_recovery >=80 , 'YES', 'NO, rerun')  #fix 

head(QAspks)

#plot spk recoveries output as a bar graph to easily check - want any over 10% to be red need to work on this 
spksbar <- ggplot(data = QAspks, aes(x = Sample_ID, y = spk_recovery)) +
        geom_bar(stat = 'identity') + 
        scale_fill_manual(values=c("lightblue4")) + 
        theme_classic() + labs(x= "Sample ID", y="Spike Recovery (%)") + 
        theme(legend.position="none") +  
        geom_hline(yintercept=80, linetype="dashed", color = "black", size=1) + 
        geom_hline(yintercept=120, linetype="dashed", color = "black", size=1)

spksbar



#check for percent of no, reruns to see if it  would warrant reruns 
Perc_spks <- QAspks %>% 
  group_by(SO4_spks_flag) %>%
  summarise(no_rows = length(SO4_spks_flag)) 
Perc_spks$Total <- length(QAspks$SO4_spks_flag)
Perc_spks$Percent <- (Perc_spks$no_rows / Perc_spks$Total)*100
head(Perc_spks)

```

## Pull out spikes and check with area calc
```{r}
#Show me the data that we have from the calculations 
head(sampledat)

#now use area of all samples and calculate undilution corrected concentrations in ug/mL
sampledat$SO4_ugmL <- ((sampledat$SO4_Area)-SO4_Int)/SO4_Slope
sampledat$Cl_ugmL <- (sampledat$Cl_Area-Cl_Int)/Cl_Slope
head(sampledat)

#pull out any rows that have "spk" in the SampleID column
spks <- sampledat %>%  
  filter(str_detect(Sample_ID, "spk"))      #have to change this to match data
head(spks)

## Only keep the columns that we need 
spks <- spks[ ,c(1,9,10)] # dont need this here 
head(spks)

#remove the spk from these IDs so we will have duplicate sample names
spks$Sample_ID<-gsub("_spk","",as.character(spks$Sample_ID))
spks <- spks[ ,c(1,2)]
colnames(spks) <- c('Sample_ID', 'SO4_ugmL_spk')
head(spks)

#put it back together with the old data set and look for duplicates 
QAspks <- merge(sampledat, spks)
head(QAspks)

#now we need to calculate the spike concentration and calculate the spike recovery
spkconc <- (250)    # in ug
spkvol <- 10             # in uL
spkvol <- spkvol/1000 
#spike for these samples was 10uL of the 250mM standard
QAspks$SO4_spk_Conc <- (spkconc)*spkvol         # mmoles of SO4 
head(QAspks)

#need to determine dilution factors and initial amount of sample added
#if your samples are all the same dilution just use the first line 
#for Steph / COMPASS this depends on the site so... 
#QAspks$Dilution <- 1
#QAspks$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "MSM_UP"), 50, QAspks$Dilution)
#$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "MSM_TR"), 50, QAspks$Dilution)
#QAspks$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "MSM_WC"), 100, QAspks$Dilution)
#$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "GCrew_UP"), 50, QAspks$Dilution)
#QAspks$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "GCrew_TR"), 50, QAspks$Dilution)
#QAspks$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "GCrew_WC"), 100, QAspks$Dilution)
#QAspks$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "GWI_UP"), 100, QAspks$Dilution)
#$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "GWI_TR"), 100, QAspks$Dilution)
#QAspks$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "GWI_WC"), 200, QAspks$Dilution)
#QAspks$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "SWH_UP"), 100, QAspks$Dilution)
#QAspks$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "SWH_TR"), 100, QAspks$Dilution)
#QAspks$Dilution <-  ifelse(str_detect(QAspks$Sample_ID, "SWH_WC"), 100, QAspks$Dilution)

#Set Sample volumes in uL 
QAspks$SampleVol <- 1
QAspks$SampleVol <-  ifelse(str_detect(QAspks$Sample_ID, "FTS_"), 1475, QAspks$SampleVol)
QAspks$SampleVol <-  ifelse(str_detect(QAspks$Sample_ID, "Aquifer"), 1501, QAspks$SampleVol)


#change sample volume to L 
QAspks$SampleVol <- QAspks$SampleVol/1000
head(QAspks)

#gives us the total SO4 in the sample in mmoles
QAspks$SO4_Total_unspkd <- QAspks$SO4_ugmL*QAspks$SampleVol

##total SO4 in spiked sample in mmoles
QAspks$SO4_Total_spkd <- (QAspks$SO4_ugmL_spk)*(QAspks$SampleVol+spkvol) 

QAspks$SO4_expctd_spkd <-  (QAspks$SO4_Total_unspkd + QAspks$SO4_spk_Conc)
QAspks$spk_recovery <-    (QAspks$SO4_Total_spkd/QAspks$SO4_expctd_spkd)*100
QAspks$SO4_spks_flag <-  ifelse(QAspks$spk_recovery <=120 & QAspks$spk_recovery >=80 , 'YES', 'NO, rerun')  #fix 

head(QAspks)

#plot spk recoveries output as a bar graph to easily check - want any over 10% to be red need to work on this 
spksbar <- ggplot(data = QAspks, aes(x = Sample_ID, y = spk_recovery)) +
        geom_bar(stat = 'identity') + 
        scale_fill_manual(values=c("lightblue4")) + 
        theme_classic() + labs(x= "Sample ID", y="Spike Recovery (%)") + 
        theme(legend.position="none") +  
        geom_hline(yintercept=80, linetype="dashed", color = "black", size=1) + 
        geom_hline(yintercept=120, linetype="dashed", color = "black", size=1)

spksbar



#check for percent of no, reruns to see if it  would warrant reruns 
Perc_spks <- QAspks %>% 
  group_by(SO4_spks_flag) %>%
  summarise(no_rows = length(SO4_spks_flag)) 
Perc_spks$Total <- length(QAspks$SO4_spks_flag)
Perc_spks$Percent <- (Perc_spks$no_rows / Perc_spks$Total)*100
head(Perc_spks)

```


## Make final dataframe with IDs  
```{r}
#for steph <- pull out identifiers of the sample names 
#pull the sample ID and separate it by the underscores 
IDs <- data.frame(do.call('rbind', strsplit(as.character(sampledat2$Sample_ID),'_',fixed=TRUE)))
colnames(IDs) <- c("Sample Number" , "Project","Time-Well", "Date", "ID", "ID1")
head(IDs)

#rejoin them to the dataframe
alldat <- cbind(IDs, sampledat2)
head(alldat)

```

## Make final dataframe with IDs  
```{r}
setwd("S:/Biogeochemistry/People/Wilson (Steph)/Data/RAD7/July 2023 Tidal Survey/Survey Data/Dionex Files")       #Change wd 

write.csv(alldat, file="GCReW_FlumeTidalSurvey_202402_SO4_Cl_PrelimData.csv")           #Change file name


```


## END
