---
title: "Synoptic CB: Lateral Transport Surveys"
author: "GCW Survey Samples"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
    number_sections: true
output_dir: "To Be Reviewed/PDF"
---

\newpage

##Run Information 
```{r run information, include=TRUE}
cat("Run Information: NAME ") #lets you know what section you're in 
#set the run date & user name 
  run_date <- "06/24/2025"
  sample_year <- "2024"
  sample_month <- "September"
  user <- "Stephanie Wilson"

#identify the files you want to read in 
  #read in as a list to accommadate ultiple runs in a month
  NOx_files <- c("Raw_GCW_Data/COMPASS_SynopticCB_LatT_GCW_NOx_1.csv", 
                 "Raw_GCW_Data/COMPASS_SynopticCB_LatT_GCW_NOx_2.csv", 
                 "Raw_GCW_Data/COMPASS_SynopticCB_LatT_GCW_NOx_3.csv")
  NH3_PO4_files <- c("Raw_GCW_Data/COMPASS_SynopticCB_LatT_GCW_NH3_PO4_1.csv",
                     "Raw_GCW_Data/COMPASS_SynopticCB_LatT_GCW_NH3_PO4_2.csv",
                     "Raw_GCW_Data/COMPASS_SynopticCB_LatT_GCW_NH3_PO4_3.csv")

# Define the file path for QAQC log file - NO Need to change just check year 
  library(here)
  file_path <- here::here("LatT_Data/Discrete_Data/QAQC_logs", "COMPASS_SynopticCB_LatT_Nutrient_QAQClog.csv")
  final_path <- "Processed_GCW_Data/GCW_Nutrients_Processed.csv"

#record any notes about the run or anything other info here: 
  run_notes <- "PO4 samples and checks run on 02/04/2024 are no good - made them NA and will replace after reruns."

#Set up file path for metadata 
  Raw_Metadata = "Raw_GCW_Data/COMPASS_SynopticCB_LatT_GCW_Discrete_Metadata.csv"

  cat(run_notes)
```

##Setup
```{r setup, include=FALSE}

#let you know which section you are in 
cat("Setup")

#a link to the Gitbook or whatever protocol you are using for this analysis 


#load/install packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  dplyr,
  purrr,
  ggplot2,
  ggpubr,
  tidyr,
  tidyverse,
  lubridate,
  tinytex,
  stringr,
  writexl,
  readr,
  readxl,
  purrr,
  tinytex,
  broom)

#Coefficients / constants that are needed for calculations 
N_mw <- 14.0067    # molecular weight of N 
P_mw <- 30.973762  # molecular weight of P 
Con1 <- 1000       # conversion factor value
Con2 <- 1000000    # conversion factor value 

#Detection limit and top standards for flagging 
NOx_dl <- 0.025  #mgL
NH3_dl <- 0.02  #mgL
PO4_dl <- 0.003 #mgL

NOx_top <- 1  #mgL
NH3_top <- 2  #mgL
PO4_top <- 0.3 #mgL

#Check Standard concnetrations 
NOx_CCV <- 0.5 
NH3_CCV <- 1.0 
PO4_CCV <- 0.15 

#Spike Concentrations 
NOx_Spk <- 0.5 #ppm or mg/L
NH3_Spk <- 1
PO4_Spk <- 0.152 

#expected ranges for sample concentrations used for flags 
r2_cutoff = 0.990
chk_flag = 0.25
chk_conc_flag = 15 #cutoff level for percent difference of check stds vs. expected concentration 
chks_flag = 60
rep_flag = 25 
#^this is a 25% error between samples
#blank_flag is calculated based on samples later in this code

#pe check Concentrations
NH3_pe <- 1.034
NOx_pe <- 1.51
PO4_pe <- 0.824

```

##Read in metadata and create similar sample IDs for matching to samples 
```{r pull in metadata for later, include=FALSE}

#read in the raw metadata file 
raw_metadata <- read.csv(Raw_Metadata)

#create project column in metadata 
metadata <- raw_metadata %>%
  mutate(Project = "LatT") %>%
   mutate(sample_id = str_replace_all(sample_id, "-", "_"))

#Create NUTR IDs from what was collected for comparison later
metadata <- metadata %>%
  mutate(NUTR_ID =   paste(Project,
                     site,
                     sample_type,
                     sample_id,
                     sep = "_"))

#Take out the columns and rows that are not relevant
nutr_metadata <- metadata %>%
  select(NUTR_ID, site, sample_type, sample_id) %>%        
  # only keep specific columns
  filter(!is.na(NUTR_ID) & NUTR_ID != "")  # remove missing/blank NUTR_ID rows


```

\newpage

## Import Data & Clean
```{r Import Data, include=FALSE}
cat("Import Data")

#set file path for data - in run info chunk 
path <- ("file path")

#Read in Raw Data 
data_NOx <- map(NOx_files, read.csv)
data_NH3_PO4 <- map(NH3_PO4_files, read.csv)

# Combining Files
df_combo <- bind_rows(data_NOx, data_NH3_PO4)

# Rename columns
df_all <- df_combo %>%
  select(Sample_Name = 4,
         Run_Number = 5,
         Conc = 6,
         Absorbance = 7,
         Dilution = 9,
         Unit = 12,
         Test = 13,
         Run_Time = 15) %>%
  mutate(Run_Number = as.numeric(Run_Number))

#Checking column headers
head(df_all)

#We need to make the PO4 data NA if it was run on the day that had the terrible std. curve bc those will need to be rerun 
df_all <- df_all %>%
  mutate(
    Run_Time1 = str_trim(as.character(Run_Time))
  )

df_all <- df_all %>%
  mutate(
    Run_Date = parse_date_time(
      Run_Time1,
      orders = c("mdy HM", "mdy HMS", "dmy HM", "dmy HMS", "ymd HM"),
      tz = "UTC"
    )
  )


df_all <- df_all %>%
  mutate(
    Run_Date = as.Date(Run_Date, format = "%d/%m/%Y %H:%M")) %>%
  mutate(
    Conc = if_else(
      Run_Date == as.Date("2025-02-04") & Test == "o-PHOS 0.3"  & grepl("LatT", Sample_Name),
      NA_real_,
      Conc
    )
  ) %>%
  mutate(
    Conc = if_else(
      Run_Date == as.Date("2025-02-04") & Test == "o-PHOS 0.3"  & grepl("Abs_Chk", Sample_Name),
      NA_real_,
      Conc
    )
  ) %>%
  select(-Run_Date, -Run_Time1)


```



## Assessing standard Curves
  #Pull out standards data  
```{r Pull out Standard Curves, echo=FALSE}
cat("Assess Standard Curves")

#Pull out standards 
stds <- df_all %>%
  filter(str_detect(Sample_Name, "Standard"))

#Making standards dataframe based on the test
stds_NOx <- stds[stds$Test == "Vanadium NOx", ]
stds_NH3 <- stds[stds$Test == "Ammonia 2", ]
stds_PO4 <- stds[stds$Test == "o-PHOS 0.3", ]


#Inputting Standard Values Based on Protocol (LINK PROTOCOL)
stds_NOx <- stds_NOx %>%
  mutate(`Conc` = case_when(
    Sample_Name == "Standard 0" ~  0.0,
    Sample_Name == "Standard 1" ~  0.0,
    Sample_Name == "Standard 90" ~ 0.0222,
    Sample_Name == "Standard 91" ~ 0.05,
    Sample_Name == "Standard 92" ~ 0.1,
    Sample_Name == "Standard 93" ~ 0.25,
    Sample_Name == "Standard 94" ~ 0.5,
    Sample_Name == "Standard 95" ~ 0.75,
    Sample_Name == "Standard 96" ~ 1.0,
    TRUE ~ `Conc`),  # leave unchanged if no match
    Run_Date = format(lubridate::mdy_hm(Run_Time), "%m-%d-%Y")) %>%
  filter(!Sample_Name %in% c("Nitrate Standard" , "Nitrite Standard"))

#ID x and y
x1 <- stds_NOx$Absorbance
y1 <- stds_NOx$Conc

stds_NH3 <- stds_NH3 %>%
  mutate(`Conc` = case_when(
    Sample_Name == "Standard 0" ~  0.0,
    Sample_Name == "Standard 1" ~  0.0,
    Sample_Name == "Standard .0389" ~ 0.0389,
    Sample_Name == "Standard .1000" ~ 0.1,
    Sample_Name == "Standard .2000" ~ 0.2,
    Sample_Name == "Standard .5000" ~ 0.5,
    Sample_Name == "Standard 1.0000" ~ 1.0,
    Sample_Name == "Standard 1.5000" ~ 1.5,
    Sample_Name == "Standard 2.0000" ~ 2,
    TRUE ~ `Conc`),  # leave unchanged if no match
    Run_Date = format(lubridate::mdy_hm(Run_Time), "%m-%d-%Y"))

# identifying x and y
x2 <- stds_NH3$Absorbance
y2 <- stds_NH3$Conc

stds_PO4 <- stds_PO4 %>%
  mutate(`Conc` = case_when(
    Sample_Name == "Standard 0" ~  0.0,
    Sample_Name == "Standard 1" ~  0.0,
    Sample_Name == "Standard 90" ~ 0.0060,
    Sample_Name == "Standard 91" ~ 0.0150,
    Sample_Name == "Standard 92" ~ 0.0300,
    Sample_Name == "Standard 93" ~ 0.0750,
    Sample_Name == "Standard 94" ~ 0.1500,
    Sample_Name == "Standard 95" ~ 0.2250,
    Sample_Name == "Standard 96" ~ 0.3000,
    TRUE ~ `Conc`),  # leave unchanged if no match
    Run_Date = format(lubridate::mdy_hm(Run_Time), "%m-%d-%Y"))

#ID x and y
x3 <- stds_PO4$Absorbance
y3 <- stds_PO4$Conc

#generating line of best fit aka standard curves
#NOx

# Fit the quadratic model
quad_reg_NOx <- lm(y1 ~ x1 + I(x1^2))

#quad_reg_NOx <- lm(Absorbance ~ Conc + Conc2, data = stds_NOx)
NOx_coefs <- coef(quad_reg_NOx)                        # intercept and slopes
NOx_r2 <- summary(quad_reg_NOx)$r.squared              # R squared
# Store in a clean dataframe
std_curve_NOx_1 <- data.frame(
  Test = "NOx",
  Intercept = NOx_coefs["(Intercept)"],
  Slope = NOx_coefs[2],
  #Conc2_Coeff = NOx_coefs["Conc2"],
  R_squared = NOx_r2
)

#NH3
lin_reg_NH3 <- lm(y2 ~ x2)
NH3_coefs <- coef(lin_reg_NH3)                        # intercept and slope
NH3_r2 <- summary(lin_reg_NH3)$r.squared              # R squared
# Store in a clean dataframe
std_curve_NH3_1 <- data.frame(
  Test = "NH3",
  Intercept = NH3_coefs["(Intercept)"],
  Slope = NH3_coefs[2],
  R_squared = NH3_r2
)

#PO4
lin_reg_PO4 <- lm(y3 ~ x3)
PO4_coefs <- coef(lin_reg_PO4)                        # intercept and slope
PO4_r2 <- summary(lin_reg_PO4)$r.squared              # R squared
# Store in a clean dataframe
std_curve_PO4_1 <- data.frame(
  Test = "PO4",
  Intercept = PO4_coefs["(Intercept)"],
  Slope = PO4_coefs[2],
  R_squared = PO4_r2
) 


#Combining standards & curve data frames
stds_combo <- bind_rows(stds_NOx, stds_NH3, stds_PO4)
std_curve_combo <- bind_rows(std_curve_NOx_1, std_curve_NH3_1, std_curve_PO4_1)


```
  #Plot standards data 
```{r Assess Standard Curves, echo=FALSE}
cat("Assess Standard Curves")

#Plot standard Curve or Curves 
  #v-Nox
std_curve_NOx <- ggplot(stds_NOx, aes(x = Conc, y = Absorbance)) +
  geom_point(size=3) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), color = "coral") +
  theme_bw() + 
  facet_wrap(~Run_Date) +
  labs(x="Concentration (ppm)",
       y="Absorbance",
       title = "NOx Standard Curve")+ 
  annotate("text", x = 0.75, y = max(stds_NOx$Absorbance), 
           label = paste("r^2 =", round(NOx_r2, 4)),
           color = "black", size = 4)
print(std_curve_NOx)

  #NH3 
std_curve_NH3 <- ggplot(stds_NH3, aes(x = Conc, y = Absorbance)) +
  geom_point(size=3) +
  geom_smooth(method = "lm", se = FALSE, color = "darkgoldenrod") +
  theme_bw() + 
  facet_wrap(~Run_Date) +
  labs(x="Concentration (ppm)",
       y="Absorbance",
       title = "NH3 Standard Curve")+ 
  annotate("text", x = 1.7, y = max(stds_NH3$Absorbance), label = paste("r^2 =", round(NH3_r2, 4)),
          color = "black", size = 4)
print(std_curve_NH3)

  #PO4 
std_curve_PO4 <- ggplot(stds_PO4, aes(x = Conc, y = Absorbance)) +
  geom_point(size=3) +
  geom_smooth(method = "lm", se = FALSE, color = "darkkhaki") +
  facet_wrap(~Run_Date) +
  theme_bw() + 
  labs(x="Concentration (ppm)",
       y="Absorbance",
       title = "PO4 Standard Curve")+ 
  annotate("text", x = 0.25, y = max(stds_PO4$Absorbance), label = paste("r^2 =", round(PO4_r2, 4)),
          color = "black", size = 4)
print(std_curve_PO4)

############## Report on Cutoffs 

#Report out a flag if the run has an R2 lower than appropriate 
#Write out to the user whether or not the r2 is above the cutoff of 0.98
  ifelse(std_curve_NOx_1$R_squared <= r2_cutoff, 
         "NOx Curve r2 is below cutoff! - REASSESS", 
         "NOx Curve r2 GOOD - PROCEED")
  ifelse(std_curve_NH3_1$R_squared <= r2_cutoff, 
         "NH3 Curve r2 is below cutoff! - REASSESS", 
         "NH3 Curve r2 GOOD - PROCEED")
  ifelse(std_curve_PO4_1$R_squared <= r2_cutoff, 
         "PO4 Curve r2 is below cutoff! - REASSESS", 
         "PO4 Curve r2 GOOD - PROCEED")
  

#check for the a slope QAQC file, if there is not one, make one 
if (file.exists(file_path)) {
  # If it exists, read it back into R
  stds_log <- read.csv(file_path)
  print("QAQC log file exists and has been read into the code.")
  } else {
  # If it does not exist, create the CSV file
  stds_log <- as.data.frame(matrix(ncol = 6, nrow = 0))
  colnames(stds_log) <- c("Test", "Intercept", "Slope", "R_squared", "run_date", "user")
  
  #maybe add here the last slopes from the previous year
  
  # Write add_log to CSV
  write.csv(stds_log, file = file_path, row.names = FALSE)
  print("QAQC log file does not exist. It has been created.")
  }
  
  #getting rid of first "X" column
  #stds_log <- stds_log %>%
  #  select(-1)
  
#create a dataframe that can be appended to the QAQC log 
add_log <- as.data.frame(bind_rows(std_curve_NOx_1, std_curve_NH3_1, std_curve_PO4_1))
add_log$run_date <- run_date
add_log$user <- user

#compare slopes to previous runs (from log) in order to assess drift 
stds_log$run_date <- as.character(stds_log$run_date)
add_log$run_date  <- as.character(add_log$run_date)     #getting the run_date column in the same type to merge

#Filter to only rows in Slopes that are NOT already in log (by run_date + analyte) but need to add if none
if (nrow(stds_log) == 0) {
  # If log is empty, everything in add_log is new
  new_rows <- add_log
} else {
  # Otherwise, compare to existing log
  new_rows <- anti_join(add_log, stds_log, by = c("run_date", "Test"))
}


# Append the new, non-duplicate rows to log
stds_log$Test <- as.character(stds_log$Test)
stds_log$user <- as.character(stds_log$user)
log <- bind_rows(stds_log, new_rows)

#Plot the slopes through time 
Slopes_chk <- ggplot(log, aes(run_date, Slope, col=Test)) + 
  geom_point(size=4) + 
  geom_line(aes(group = Test)) + 
  theme_bw() + 
  labs(title="Slope Drift Assessment", x="Run Date", y="Slope") +
  scale_color_manual(values=c("coral", "darkgoldenrod", "darkkhaki"))
Slopes_chk

#averaging the slopes from the log and printing
avg_slopes <- log %>%
  group_by(Test) %>%
  summarise(avg_slope = mean(Slope, na.rm = TRUE))
knitr::kable(avg_slopes, caption = "Average Slope by Analyte", digits = 3)


#write out the log file with the added lines for this run date 
write.csv(log, file_path)

#write out a flag to the sample dataframe if the r2 is above the cutoff of 0.98
df_all <- df_all %>%
  mutate(
    NOx_flag = if (NOx_r2 <= r2_cutoff) {
      "NOx r2 low"
    } else {
      ""
    },
    NH3_flag = if (NH3_r2 <= r2_cutoff) {
      "NH3 r2 low"
    } else {
      ""
    },
    PO4_flag = if (PO4_r2 <= r2_cutoff) {
      "PO4 r2 low"
    } else {
      ""
    }
  )



```
 
 \newpage


## Dilution Corrections - ensure the latest dilution is kept
```{r Dilution Corrections, echo=FALSE}

cat("Dilution Corrections")

#Calculate the concentration when accounting for the dilution factor if applicable

#checking to see if duplicate samples (mislabeled/wrongly inputted/reran)
df_duplicates <- df_all %>%
  filter(!if_all(everything(), is.na)) %>%  # Remove rows that are entirely NA

  # Exclude common QC sample names and standard patterns
  filter(
    !(Sample_Name %in% c(
      "Duplicate", "CCV", "CCB", "1mg/L ammonia", "DI",
      "Blank", "Auto Spike", "0.15 mg/L"
    )) &
    !startsWith(Sample_Name, "Standard ") &
    !startsWith(Sample_Name, "Nitrite ") &
    !startsWith(Sample_Name, "Nitrate ") &
    !startsWith(Sample_Name, "Abs_Chk_") &
    !startsWith(Sample_Name, "peChk_") &
    !grepl("^\\d{1,2}/\\d{1,2}/\\d{4}\\s+\\d{1,2}:\\d{2}$", Sample_Name) &  # Remove timestamp-like names
    !grepl("^\\d+$", Sample_Name) &  # Remove sample names that are just numbers
    !is.na(Sample_Name) & Sample_Name != ""  # 🔍 Remove blank or missing names
  ) %>%
  group_by(Test, Sample_Name) %>%  # Group by test and sample
  filter(n() > 1) %>%              # Keep only those that appear more than once
  ungroup()

#pulling them out into a string and printing them out
dil_dups_string <- df_duplicates %>%
  distinct(Sample_Name) %>%
  pull(Sample_Name) %>%
  paste(collapse = ", ")

# Make sure Dilution is numeric
df_duplicates$Dilution <- as.numeric(df_duplicates$Dilution)

# Report duplicated samples
if (dil_dups_string != "") {
  message("Duplicated samples: ", dil_dups_string)

  bad_dups <- df_duplicates %>%
    group_by(Test, Sample_Name) %>%
    summarise(
      n_dups = n(),
      any_dilution = any(Dilution > 1, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    filter(!any_dilution)

  if (nrow(bad_dups) > 0) {
    cat("\nWARNING: Duplicated samples with NO dilution (possible input error):\n")
    print(bad_dups)
  } else {
    cat("\n All duplicated samples have valid dilutions. No naming issues detected.\n")
  }

} else {
  message("No duplicated samples.")
}





df_all_cor <- df_all %>%
  arrange(row_number()) %>%
  mutate(
    Dilution = case_when(
      Dilution == "0" ~ 1.0,
      TRUE ~ as.numeric(Dilution)
    ),
    Pair_ID = ifelse(
      grepl("Duplicate", Sample_Name, ignore.case = TRUE),
      paste0(lag(Sample_Name), "_", lag(Run_Number)),  # pair only if same run
      paste0(Sample_Name, "_", Run_Number)
    ),
    Original_Name = Sample_Name
  ) %>%
  group_by(Pair_ID, Test, Run_Number) %>%  # group by Pair_ID, Test, and Run_Number
  filter(
    Dilution == ifelse(any(Dilution > 1, na.rm = TRUE), max(Dilution, na.rm = TRUE), 1)
  ) %>%
  ungroup()




```


## Performance Check
```{r pe Check, echo = FALSE}

NOx_peChk <- df_all_cor %>%
  filter(Test == "Vanadium NOx", 
         str_detect(Sample_Name, "peChk_NOx")) %>%
  summarise(
    Mean_Chk_Conc = mean(Conc, na.rm = TRUE),
    SD_Chk_Conc = sd(Conc, na.rm = TRUE),
    CV = (SD_Chk_Conc / Mean_Chk_Conc) * 100,
    pct_diff_Chk = abs(Mean_Chk_Conc - NOx_pe) / NOx_pe,
    NOx_pe_flag = ifelse(abs(pct_diff_Chk) < 25, "YES, Pass", "NO, rerun"))
      

NH3_peChk <- df_all_cor %>%
  filter(Test == "Ammonia 2", 
         str_detect(Sample_Name, "peChk_")) %>%
  summarise(
    Mean_Chk_Conc = mean(Conc, na.rm = TRUE),
    SD_Chk_Conc = sd(Conc, na.rm = TRUE),
    CV = (SD_Chk_Conc / Mean_Chk_Conc) * 100,
    pct_diff_Chk = abs(Mean_Chk_Conc - NH3_pe) / NH3_pe,
    NH3_pe_flag = ifelse(abs(pct_diff_Chk) < 25, "YES, Pass", "NO, rerun"))

PO4_peChk <- df_all_cor %>%
  filter(Test == "o-PHOS 0.3", 
         str_detect(Sample_Name, "peChk_")) %>%
  summarise(
    Mean_Chk_Conc = mean(Conc, na.rm = TRUE),
    SD_Chk_Conc = sd(Conc, na.rm = TRUE),
    CV = (SD_Chk_Conc / Mean_Chk_Conc) * 100,
    pct_diff_Chk = abs(Mean_Chk_Conc - PO4_pe) / PO4_pe,
    PO4_pe_flag = ifelse(abs(pct_diff_Chk) < 25, "YES, Pass", "NO, rerun"))
  


#flag write out 
ifelse(NOx_peChk$pct_diff_Chk >= chk_flag, 
       "NOx pe Check has a % Difference >25% - REASSESS",  
       "NOx pe Check has a % Difference <25% - PROCEED")
cat("Run mean =", NOx_peChk$Mean_Chk_Conc, "\n")
cat("Expected  =", NOx_pe, "\n\n")
ifelse(NH3_peChk$pct_diff_Chk >= chk_flag, 
       "NH3 pe Check has a % Difference >25% - REASSESS",  
       "NH3 pe Check has a % Difference <25% - PROCEED")
cat("Run mean =", NH3_peChk$Mean_Chk_Conc, "\n")
cat("Expected  =", NH3_pe, "\n\n")
ifelse(PO4_peChk$pct_diff_Chk >= chk_flag, 
       "PO4 pe Check has a % Difference >25% - REASSESS",  
       "PO4 pe Check has a % Difference <25% - PROCEED")
cat("Run mean =", PO4_peChk$Mean_Chk_Conc, "\n")
cat("Expected  =", PO4_pe, "\n")




```

 
##Check NOx Reduction Efficiency 
```{r Assess reduction Efficiency, echo=FALSE}
cat("Assess Reduction Efficiency")

#check on the reduction efficiency for the NOx test: 
#Pull out test stds 
red_eff <- df_all %>%
  filter(Sample_Name %in% c("Nitrate Standard", "Nitrite Standard"))

red_eff$Eff_Percent <- (red_eff$Conc / 0.5)*100
red_eff$Eff_flag <-  ifelse(red_eff$Eff_Percent >= 90, 'YES', 'NO, rerun')

red_eff <- red_eff %>%
  mutate(row_num = row_number())

#Plot these efficencies 
red_effs_plot <-  ggplot(data = red_eff, aes(x = factor(row_num), y = Conc, fill=Eff_flag)) +
       geom_bar(stat = 'identity') + 
       facet_wrap(~Sample_Name) +
       scale_fill_manual(values = c("YES" = "midnightblue", "NO, rerun" = "darkred")) +
       theme_classic() + labs(x= " ", y="NOx (mg/L)", title=" ") + 
       theme(legend.position="bottom") +  
       geom_hline(yintercept= 0.5, linetype="dashed", 
                color = "black", linewidth=1)  + 
       guides(fill=guide_legend(title="Reduction Efficiency >90%"))+
      scale_x_discrete(drop = TRUE)
print(red_effs_plot)

#create a flag 
NOx_mean_red_eff <- mean(red_eff$Eff_Percent)

#report out if flags indicate need for rerun and what the value is
ifelse(NOx_mean_red_eff >= 95,
       "Mean NOx Reduction Efficiency >95% - PROCEED",
       "Mean NOx Reduction Efficiency <95% - REASSESS")
print(NOx_mean_red_eff)

#write out a flag to the sample dataframe if red eff is low
if (NOx_mean_red_eff <= 95) {
    df_all$NOx_flag <- ifelse(
    df_all$NOx_flag != "",
    paste0(df_all$NOx_flag, "; NOx reduction efficiency low"),
    "NOx reduction efficiency low")}

```

\newpage

## Analyze the Check Standards
```{r Check Standards, echo=FALSE}

cat("Analyze Check Standards")

#Pull out check standards from raw file 
NOx_chks <- df_all %>%
  filter(str_detect(Sample_Name, "CCV"))%>% 
  mutate(rep = row_number())

NH3_chks <- df_all %>%
  filter(str_detect(Sample_Name, "1mg/L ammonia"))%>% 
  mutate(rep = row_number())

PO4_chks <- df_all %>%
  filter(str_detect(Sample_Name, "0.15 mg/L"))%>% 
  mutate(rep = row_number())


#RSV of standards 
chks_NOx_rsv <- ((sd(NOx_chks$Conc))/mean(NOx_chks$Conc))
chks_NH3_rsv <- ((sd(NH3_chks$Conc))/mean(NH3_chks$Conc))
chks_PO4_rsv <- ((sd(PO4_chks$Conc))/mean(PO4_chks$Conc))

#write out to user about whether or not to continue 
ifelse(chks_NOx_rsv >= chk_flag, 
       "NOx CHECK STANDARD RSD TOO HIGH - REASSESS",
       "NOx Check Standard RSD within Range - PROCEED")
ifelse(chks_NH3_rsv >= chk_flag, 
       "NH3 CHECK STANDARD RSD TOO HIGH - REASSESS",
       "NH3 Check Standard RSD within Range - PROCEED")
ifelse(chks_PO4_rsv >= chk_flag, 
       "PO4 CHECK STANDARD RSD TOO HIGH - REASSESS",
       "PO4 Check Standard RSD within Range - PROCEED")


#calculate percent difference between check standards & expected concentration 
#flag if the percent difference is over X% (defined in setup)
#calculate percent difference of check standards 
NOx_chks$NOx_diff <- ((NOx_chks$Conc - NOx_CCV)/((NOx_chks$Conc + NOx_CCV)/2)) * 100
NOx_chks$NOx_diff_flag <-  ifelse(NOx_chks$NOx_diff <= chk_conc_flag, 'YES', 'NO, rerun')

NH3_chks$NH3_diff <- ((NH3_chks$Conc - NH3_CCV)/((NH3_chks$Conc + NH3_CCV)/2)) * 100
NH3_chks$NH3_diff_flag <-  ifelse(NH3_chks$NH3_diff <= chk_conc_flag, 'YES', 'NO, rerun')

PO4_chks$PO4_diff <- ((PO4_chks$Conc - PO4_CCV)/((PO4_chks$Conc + PO4_CCV)/2)) * 100
PO4_chks$PO4_diff_flag <-  ifelse(PO4_chks$PO4_diff <= chk_conc_flag, 'YES', 'NO, rerun')


#plot the check standards
NOx_chks_plot <-  ggplot(data = NOx_chks, aes(x = rep, y = Conc, fill=NOx_diff_flag)) +
       geom_bar(stat = 'identity') + 
        scale_fill_manual(values = c("YES" = "chartreuse4", "NO, rerun" = "darkred")) +
        labs(x= " ", y="NOx (mg/L)", title="Check Stds: NOx") + 
        theme(legend.position="bottom") +  
        geom_hline(yintercept=NOx_CCV,
              linetype="dashed", color = "black", linewidth=1) + 
        guides(fill=guide_legend(title="% Difference <10%")) +
        theme_classic()

NH3_chks_plot <-  ggplot(data = NH3_chks, aes(x = rep, y = Conc, fill=NH3_diff_flag)) +
       geom_bar(stat = 'identity') + 
       scale_fill_manual(values = c("YES" = "chartreuse4", "NO, rerun" = "darkred")) +
       theme_classic() + 
       labs(x= " ", y="NH3  (mg/L)", title="Check Stds: NH3") + 
       theme(legend.position="bottom") +  
       geom_hline(yintercept=NH3_CCV,
              linetype="dashed",  color = "black", linewidth=1) + 
       guides(fill=guide_legend(title="% Difference <10%"))

PO4_chks_plot <-  ggplot(data = PO4_chks, aes(x = rep, y = Conc, fill=PO4_diff_flag)) +
       geom_bar(stat = 'identity') + 
       scale_fill_manual(values = c("YES" = "chartreuse4", "NO, rerun" = "darkred")) +
        theme_classic() + labs(x= " ", y="PO4  (mg/L)", title="Check Stds: PO4") + 
        theme(legend.position="bottom") +  geom_hline(yintercept=PO4_CCV,
              linetype="dashed",  color = "black", linewidth=1) + 
        guides(fill=guide_legend(title="% Difference <10%"))

#Combined Plot
Chk_Std_Plots <- ggarrange(
  NOx_chks_plot, 
  NH3_chks_plot, 
  PO4_chks_plot,   
  nrow = 1, 
  ncol = 3,
  common.legend = TRUE,
  legend = "bottom")
print(Chk_Std_Plots)

#calculate the percent of check standards that are within the range based on the flag 
NOx_chks_percent <- (sum(NOx_chks$NOx_diff_flag == "YES")/nrow(NOx_chks))*100
NH3_chks_percent <- (sum(NH3_chks$NH3_diff_flag == "YES")/nrow(NH3_chks))*100
PO4_chks_percent <- (sum(PO4_chks$PO4_diff_flag == "YES")/nrow(PO4_chks))*100

#report out if flags indicate need for rerun
ifelse(NOx_chks_percent >= chks_flag, 
       ">60% of NOx Check Standards are within range of expected concentration - PROCEED",
       "<60% of NOx Check Standards are within range of expected concentration - REASSESS")
ifelse(NH3_chks_percent >= chks_flag,
       ">60% of NH3 Check Standards are within range of expected concentration - PROCEED",
       "<60% of NH3 Check Standards are within range of expected concentration - REASSESS")
ifelse(PO4_chks_percent >= chks_flag,
       ">60% of PO4 Check Standards are within range of expected concentration - PROCEED",
       "<60% of PO4 Check Standards are within range of expected concentration - REASSESS")


#write out a flag to the sample dataframe if less than 60% of the checks are within the expected CV
if (NOx_chks_percent <= chks_flag) {
    df_all_cor$NOx_flag <- ifelse(
    df_all_cor$NOx_flag != "",
    paste0(df_all_cor$NOx_flag, "; NOx checks out of range"),
    "NOx checks out of range"
  )
}

if (NH3_chks_percent <= chks_flag) {  
    df_all_cor$NH3_flag <- ifelse(
    df_all_cor$NH3_flag != "",
    paste0(df_all_cor$NH3_flag, "; NH3 checks out of range"),
    "NH3 checks out of range"
  )
}

if (PO4_chks_percent <= chks_flag) {  
    df_all_cor$PO4_flag <- ifelse(
    df_all_cor$PO4_flag != "",
    paste0(df_all_cor$PO4_flag, "; PO4 checks out of range"),
    "PO4 checks out of range"
  )
}



```

\newpage

## Analyze Blanks 
```{r Analyze Blanks, echo=FALSE}

cat("Assess Blanks")

#Pull out check standards from raw file 
NOx_blks <- df_all %>%
  filter(str_detect(Sample_Name, "CCB"))%>% 
  mutate(rep = row_number())

NH3_blks <- df_all %>%
  filter(Test == "Ammonia 2")%>% 
  filter(str_detect(Sample_Name, "Blank"))%>% 
  mutate(rep = row_number())

PO4_blks <- df_all %>%
  filter(Test == "o-PHOS 0.3")%>% 
  filter(str_detect(Sample_Name, "Blank"))%>% 
  mutate(rep = row_number())

#Pull out samples from df_all to calc quantile
samples <- df_all %>%  
  filter(str_detect(Sample_Name, c("GCW|GWI|MSM|SWH"))) 

#Calculating the lowest 25% of sample concentrations to compare to the blank concentrations
NOx_only <- samples %>%
  filter(Test == "Vanadium NOx")
blk_flag_NOx <- quantile(NOx_only$Conc, prob=c(.25), na.rm = TRUE)   #this gives you the lower 25% quartile of the data 
blk_flag_NOx <- ifelse(blk_flag_NOx < NOx_dl, 0.0125, blk_flag_NOx) #this will determine if the Q1 of samples is below the detection limit, if it is then it will replace the flag with half of the detection limit 
NOx_blks$NOx_diff_flag <-  ifelse(NOx_blks$Conc <= blk_flag_NOx, 'YES', 'NO, rerun')

NH3_only <- samples %>%
  filter(Test == "Ammonia 2")
blk_flag_NH3 <- quantile(NH3_only$Conc, prob=c(.25))   #this gives you the lower 25% quartile of the data 
NH3_blks$NH3_diff_flag <-  ifelse(NH3_blks$Conc <= blk_flag_NH3, 'YES', 'NO, rerun')

PO4_only <- samples %>%
  filter(Test == "o-PHOS 0.3")
blk_flag_PO4 <- quantile(PO4_only$Conc, prob=c(.25), na.rm=TRUE)   #this gives you the lower 25% quartile of the data 
PO4_blks$PO4_diff_flag <-  ifelse(PO4_blks$Conc <= blk_flag_PO4, 'YES', 'NO, rerun')

#calculate the percent of check standards that are within the range based on the flag 
NOx_blks_percent <- (sum(NOx_blks$NOx_diff_flag == "YES")/nrow(NOx_blks))*100
NH3_blks_percent <- (sum(NH3_blks$NH3_diff_flag == "YES")/nrow(NH3_blks))*100
PO4_blks_percent <- (sum(PO4_blks$PO4_diff_flag == "YES")/nrow(PO4_blks))*100

#report out if flags indicate need for rerun
ifelse(NOx_blks_percent >= 60,
       ">60% of NOx Blanks are below the lower 25% quartile of samples or 1/2 detection limit - PROCEED",
       "<60% of NOx blaks are lower 25% quartile of samples or 1/2 the detection limit - REASSESS")
ifelse(NH3_blks_percent >= 60,
       ">60% of NH3 Blanks are below the lower 25% quartile of samples - PROCEED",
       "<60% of NH3 blaks are lower 25% quartile of samples - REASSESS")
ifelse(PO4_blks_percent >= 60,
       ">60% of PO4 Blanks  are below the lower 25% quartile of samples- PROCEED",
       "<60% of PO4 blaks are lower 25% quartile of samples - REASSESS")

#plotting the blanks compared to the lower 25% of conc (what the flag is)
NOx_blks_plot <-  ggplot(data = NOx_blks, aes(x = rep, y = Conc, fill=NOx_diff_flag)) +
       geom_bar(stat = 'identity') + 
       scale_fill_manual(values = c("YES" = "deepskyblue3", "NO, rerun" = "darkred")) +
       theme_classic() + labs(x= " ", y="NOx (mg/L)", title="NOx Blanks") + 
       theme(legend.position="bottom") +  
       geom_hline(yintercept= as.numeric(blk_flag_NOx), linetype="dashed", 
                color = "black", linewidth=1)  + 
       guides(fill=guide_legend(title="Blank Conc <25% Quartile Samples"))

NH3_blks_plot <-  ggplot(data = NH3_blks, aes(x = rep, y = Conc, fill=NH3_diff_flag)) +
       geom_bar(stat = 'identity') + 
       scale_fill_manual(values = c("YES" = "deepskyblue3", "NO, rerun" = "darkred")) +
       theme_classic() + labs(x= " ", y="NH3  (mg/L)", title="NH3 Blanks") + 
       theme(legend.position="bottom") +  
       geom_hline(yintercept=as.numeric(blk_flag_NH3), linetype="dashed",
                color = "black", linewidth=1)  + 
       guides(fill=guide_legend(title="Blank Conc <25% Quartile Samples"))

PO4_blks_plot <-  ggplot(data = PO4_blks, aes(x = rep, y = Conc, fill=PO4_diff_flag)) +
       geom_bar(stat = 'identity') + 
       scale_fill_manual(values = c("YES" = "deepskyblue3", "NO, rerun" = "darkred")) +
       theme_classic() + labs(x= " ", y="PO4 (mg/L)", title="PO4 Blanks") + 
       theme(legend.position="bottom") +  
       geom_hline(yintercept=as.numeric(blk_flag_PO4), linetype="dashed", 
                color = "black", linewidth=1)  + 
       guides(fill=guide_legend(title="Blank Conc <25% Quartile Samples"))

#Combined Plot
Blks_Plots <- ggarrange(
  NOx_blks_plot, 
  NH3_blks_plot, 
  PO4_blks_plot,   # (you had NH3 twice!)
  nrow = 1, 
  ncol = 3,
  common.legend = TRUE,
  legend = "bottom")
print(Blks_Plots)


#find average of run blanks for flagging samples later 

# Compute averages
blk_avg_NOx <- mean(NOx_blks$Conc, na.rm = TRUE)
blk_avg_NH3 <- mean(NH3_blks$Conc, na.rm = TRUE)
blk_avg_PO4 <- mean(PO4_blks$Conc, na.rm = TRUE)

# Create a data frame
blank_avgs <- data.frame(
  Test = c("NOx", "NH3", "PO4"),
  Blank_Mean_Conc = c(blk_avg_NOx, blk_avg_NH3, blk_avg_PO4)
)

# Pretty print
knitr::kable(blank_avgs, caption = "Mean Concentration of Blanks", digits = 4)


#write out a flag to the sample dataframe if more than 60% of the blanks are above the lower 25% quantile of samples
if (NOx_blks_percent <= chks_flag) {
    df_all_cor$NOx_flag <- ifelse(
    df_all_cor$NOx_flag != "",
    paste0(df_all_cor$NOx_flag, "; NOx blanks out of range"),
    "NOx blanks out of range"
  )
}

if (NH3_blks_percent <= chks_flag) {  # assuming you have tn_chks_percent similarly
    df_all_cor$NH3_flag <- ifelse(
    df_all_cor$NH3_flag != "",
    paste0(df_all_cor$NH3_flag, "; NH3 blanks out of range"),
    "NH3 blanks out of range"
  )
}

if (PO4_blks_percent <= chks_flag) {  # assuming you have tn_chks_percent similarly
    df_all_cor$PO4_flag <- ifelse(
    df_all_cor$PO4_flag != "",
    paste0(df_all_cor$PO4_flag, "; PO4 blanks out of range"),
    "PO4 blanks out of range"
  )
}

```

\newpage

## Analyze Duplicates
```{r Analyze Duplicates, echo=FALSE}

cat("Analyze Duplicates")

#Getting dataframe of just duplicated samples
df_NOx_dup <- df_all_cor %>%
  filter(Test == "Vanadium NOx") %>%
  filter(
     !grepl("CCV|CCB|Standard|Auto Spike|Abs_Chk_20ppt|Abs_Chk_10ppt", Sample_Name, ignore.case = TRUE), 
     #^removes autospice, ccv, ccb, standards
     !is.na(Sample_Name),                                         # Remove NA
     !grepl("^\\d+$", Sample_Name),                               # removes all numbers
     !grepl("^\\d{1,2}/\\d{1,2}/\\d{2,4}", Sample_Name)) %>%      # removes all date/time
  mutate(`Duplicate?` = if_else(                                  # adds duplicate column
     grepl("Duplicate", Sample_Name, ignore.case = TRUE),         # keeps sample ID if there
     lag(Sample_Name),                                            # get previous row's SampleID
     Sample_Name)) %>%                                            # keeps sample ID if not duplicate
  group_by(`Duplicate?`) %>%                                      # groups by duplicate 
  filter(n() > 1) %>%                                             # filters anything that appears more than once 
  ungroup() %>%                          
  transmute(   
     Pair_ID = `Duplicate?`,                                      # changing heading to pair_id
     Sample_Name,                                                 #keeping sample name and conc
     Conc,                                                        #if sample name duplicate then put duplicate 
     Type = if_else(str_detect(Sample_Name, "Duplicate"), "Duplicate", "Original"))  #, if not put original to ID 
  
df_NH3_dup <- df_all_cor %>%
  filter(Test == "Ammonia 2") %>%
  filter(
     !grepl("CCV|CCB|Blank|1mg/L ammonia|Abs_Chk_20ppt|Abs_Chk_10ppt|Standard|Auto Spike", Sample_Name, ignore.case = TRUE), 
     #^removes autospice, ccv, ccb, standards
     !is.na(Sample_Name),                                         # Remove NA
     !grepl("^\\d+$", Sample_Name),                               # removes all numbers
     !grepl("^\\d{1,2}/\\d{1,2}/\\d{2,4}", Sample_Name)) %>%      # removes all date/time
  mutate(`Duplicate?` = if_else(                                  # adds duplicate column
     grepl("Duplicate", Sample_Name, ignore.case = TRUE),         # keeps sample ID if there
     lag(Sample_Name),                                            # get previous row's SampleID
     Sample_Name)) %>%                                            # keeps sample ID if not duplicate
  group_by(`Duplicate?`) %>%                                      # groups by duplicate 
  filter(n() > 1) %>%                                             # filters anything that appears more than once 
  ungroup() %>%                      
  transmute(   
     Pair_ID = `Duplicate?`,                                      # changing heading to pair_id
     Sample_Name,                                                 #keeping sample name and conc
     Conc,                                                        #if sample name duplicate then put duplicate 
     Type = if_else(str_detect(Sample_Name, "Duplicate"), "Duplicate", "Original"))  #, if not put original to ID 

df_PO4_dup <- df_all_cor %>%
  filter(Test == "o-PHOS 0.3") %>%
  filter(
     !grepl("CCV|CCB|Standard|Auto Spike|Blank|1mg/L ammonia|Abs_Chk_20ppt|Abs_Chk_10ppt|	
0.15 mg/L", Sample_Name, ignore.case = TRUE), 
     #^removes autospice, ccv, ccb, standards
     !is.na(Sample_Name),                                         # Remove NA
     !grepl("^\\d+$", Sample_Name),                               # removes all numbers
     !grepl("^\\d{1,2}/\\d{1,2}/\\d{2,4}", Sample_Name)) %>%      # removes all date/time
  mutate(`Duplicate?` = if_else(                                  # adds duplicate column
     grepl("Duplicate", Sample_Name, ignore.case = TRUE),         # keeps sample ID if there
     lag(Sample_Name),                                            # get previous row's SampleID
     Sample_Name)) %>%                                            # keeps sample ID if not duplicate
  group_by(`Duplicate?`) %>%                                      # groups by duplicate 
  filter(n() > 1) %>%                                             # filters anything that appears more than once 
  ungroup() %>%                      
  transmute(   
     Pair_ID = `Duplicate?`,                                      # changing heading to pair_id
     Sample_Name,                                                 #keeping sample name and conc
     Conc,                                                        #if sample name duplicate then put duplicate 
     Type = if_else(str_detect(Sample_Name, "Duplicate"), "Duplicate", "Original")) 

# Duplicate Stats
Nox_dup_chk <- df_NOx_dup %>%
  group_by(Pair_ID) %>%  # Use Pair_ID as it groups Originals and Duplicates
  filter(n_distinct(Type) == 2) %>%  # Keep only groups that have both Original and Duplicate
  summarise(
    OG_Conc = Conc[Type == "Original"],
    Dup_Conc = Conc[Type == "Duplicate"],
    Mean_Conc = mean(c(OG_Conc, Dup_Conc)),
    SD_Conc = sd(c(OG_Conc, Dup_Conc)),
    CV = (SD_Conc / Mean_Conc) * 100,
    pct_diff = abs(Dup_Conc - OG_Conc) / Mean_Conc * 100,
    NOx_diff_flag = ifelse(abs(CV) < 10, "YES", "NO, rerun"),
    .groups = "drop") 

NH3_dup_chk <- df_NH3_dup %>%
  group_by(Pair_ID) %>%  # Use Pair_ID as it groups Originals and Duplicates
  filter(n_distinct(Type) == 2) %>%  # Keep only groups that have both Original and Duplicate
  summarise(
    OG_Conc = Conc[Type == "Original"],
    Dup_Conc = Conc[Type == "Duplicate"],
    Mean_Conc = mean(c(OG_Conc, Dup_Conc)),
    SD_Conc = sd(c(OG_Conc, Dup_Conc)),
    CV = (SD_Conc / Mean_Conc) * 100,
    pct_diff = abs(Dup_Conc - OG_Conc) / Mean_Conc * 100,
    NH3_diff_flag = ifelse(abs(CV) < 10, "YES", "NO, rerun"),
    .groups = "drop") 

PO4_dup_chk <- df_PO4_dup %>%
  group_by(Pair_ID) %>%  # Use Pair_ID as it groups Originals and Duplicates
  filter(n_distinct(Type) == 2) %>%  # Keep only groups that have both Original and Duplicate
  summarise(
    OG_Conc = Conc[Type == "Original"],
    Dup_Conc = Conc[Type == "Duplicate"],
    Mean_Conc = mean(c(OG_Conc, Dup_Conc)),
    SD_Conc = sd(c(OG_Conc, Dup_Conc)),
    CV = (SD_Conc / Mean_Conc) * 100,
    pct_diff = abs(Dup_Conc - OG_Conc) / Mean_Conc * 100,
    PO4_diff_flag = ifelse(abs(CV) < 10, "YES", "NO, rerun"),
    .groups = "drop") 

#check to see if NOx dups are below the detection limit, this is very common for NOx and leads to 
# very high cvs between dups, so we will accept them if the samples are below detection 
Nox_dup_chk <- Nox_dup_chk %>%
  mutate(NOx_diff_flag = ifelse(OG_Conc < NOx_dl, "bdl", NOx_diff_flag))

#calculate the percent of check standards that are within the range based on the flag 
NOx_dup_percent <- (sum(Nox_dup_chk$NOx_diff_flag %in% c("YES", "bdl")) / nrow(Nox_dup_chk)) * 100
NH3_dup_percent <- (sum(NH3_dup_chk$NH3_diff_flag == "YES")/nrow(NH3_dup_chk))*100
PO4_dup_percent <- (sum(PO4_dup_chk$PO4_diff_flag == "YES", na.rm=TRUE)/nrow(PO4_dup_chk))*100

#dup flag report out
ifelse(NOx_dup_percent >= chks_flag, 
       ">60% of NOx Duplicates have a CV <10% - PROCEED",
       "<60% of NOx Duplicates have a CV <10% - REASSESS")
ifelse(NH3_dup_percent >= chks_flag, 
       ">60% of NH3 Duplicates have a CV <10% - PROCEED",
       "<60% of NH3 Duplicates have a CV <10% - REASSESS")
ifelse(PO4_dup_percent >= chks_flag, 
       ">60% of PO4 Duplicates have a CV <10% - PROCEED",
       "<60% of PO4 Duplicates have a CV <10% - REASSESS")

#Create row numbers for plotting
Nox_dup_chk <- Nox_dup_chk %>%
  mutate(row_num = row_number())

NH3_dup_chk <- NH3_dup_chk %>%
  mutate(row_num = row_number())

PO4_dup_chk <- PO4_dup_chk %>%
  mutate(row_num = row_number())

#plot dups output as a bar graph to easily check - want any over 10% to be red need to work on this 
NOx_dups_plot <- ggplot(data =Nox_dup_chk, aes(x =Pair_ID, y =CV, fill=NOx_diff_flag)) +
        geom_bar(stat = 'identity') + 
        theme_classic() + 
        labs(x= "Sample ID", y="CV between dups", title = "NOx Duplicates") + 
        scale_fill_manual(values = c("bdl" = "darkslateblue","YES" = "darkslateblue",  "NO, rerun" = "darkred")) +
        theme(legend.position="none") +  
        geom_hline(yintercept=10, linetype="dashed", 
            color = "black", size=1)  + 
        guides(fill=guide_legend(title="<10%:"))+
        theme(axis.text.x = element_text(angle = 90, hjust = 0.5))

NH3_dups_plot <- ggplot(data = NH3_dup_chk, aes(x =Pair_ID, y =CV, fill=NH3_diff_flag)) +
        geom_bar(stat = 'identity') + 
        theme_classic() + 
        labs(x= "Sample ID", y="CV between dups", title = "NH3 Duplicates") + 
        scale_fill_manual(values = c("YES" = "darkslateblue", "NO, rerun" = "darkred")) +
        theme(legend.position="none") +  
        geom_hline(yintercept=10, linetype="dashed", 
              color = "black", size=1) + 
        guides(fill=guide_legend(title="<10%:"))+
        theme(axis.text.x = element_text(angle = 90, hjust = 0.5))

PO4_dups_plot <- ggplot(data =PO4_dup_chk, aes(x =Pair_ID, y =CV, fill=PO4_diff_flag)) +
       geom_bar(stat = 'identity') + 
       theme_classic() + 
        labs(x= "Sample ID", y="CV between dups", title = "PO4 Duplicates") + 
       scale_fill_manual(values = c("YES" = "darkslateblue", "NO, rerun" = "darkred")) +
       theme(legend.position="none") +  
       geom_hline(yintercept=10, linetype="dashed", 
                color = "black", size=1) + 
        guides(fill=guide_legend(title="<10%:"))+
        theme(axis.text.x = element_text(angle = 90, hjust = 0.5))

#Combined Plot
Dups_Plots <- ggarrange(
  NOx_dups_plot, 
  NH3_dups_plot, 
  PO4_dups_plot,  
  nrow = 1, 
  ncol = 3,
  common.legend = FALSE,
  legend = "bottom")
print(Dups_Plots)

#write out a flag to the sample dataframe if more than 60% of the dups have CVs out of range 
if (NOx_dup_percent <= chks_flag) {
    df_all_cor$NOx_flag <- ifelse(
    df_all_cor$NOx_flag != "",
    paste0(df_all_cor$NOx_flag, "; NOx dups out of range"),
    "NOx dups out of range"
  )
}

if (NH3_dup_percent <= chks_flag) {  # assuming you have tn_chks_percent similarly
    df_all_cor$NH3_flag <- ifelse(
    df_all_cor$NH3_flag != "",
    paste0(df_all_cor$NH3_flag, "; NH3 dups out of range"),
    "NH3 dups out of range"
  )
}

if (PO4_dup_percent <= chks_flag) {  # assuming you have tn_chks_percent similarly
    df_all_cor$PO4_flag <- ifelse(
    df_all_cor$PO4_flag != "",
    paste0(df_all_cor$PO4_flag, "; PO4 dups out of range"),
    "PO4 dups out of range"
  )
}



```

\newpage

## Spikes
```{r Analyze Spikes, echo=FALSE}

#getting spikes and samples pulled 
df_NOx_spk <- df_all_cor %>%
  filter(Test == "Vanadium NOx") %>%
  filter(
     !grepl("CCV|CCB|Standard|Duplicate", Sample_Name, ignore.case = TRUE),
     #^removes dup, ccv, ccb, standards
     !is.na(Sample_Name),                                     # Remove NA
     !grepl("^\\d+$", Sample_Name),                           # removes all numbers
     !grepl("^\\d{1,2}/\\d{1,2}/\\d{2,4}", Sample_Name)) %>%  # removes all date/time
  mutate(`Spike?` = if_else(                                  # adds duplicate column
     grepl("Auto Spike", Sample_Name, ignore.case = TRUE),    # keeps sample ID if there
     lag(Sample_Name),                                        # get previous row's SampleID
     Sample_Name)) %>%                                        # keeps sample ID if not duplicate
  group_by(`Spike?`) %>%                                      # groups by duplicate
  filter(n() > 1) %>%                                         # filters anything that appears more than once
  ungroup()  %>%
  transmute(
    Pair_ID = `Spike?`,
    Sample_Name,
    Conc,
    Type = if_else(str_detect(Sample_Name, "Auto Spike"), "Auto_Spike", "Original"))
 
df_NH3_spk <- df_all_cor %>%
  filter(Test == "Ammonia 2") %>%
  filter(
     !grepl("CCV|CCB|Blank|1mg/L ammonia|Standard|Duplicate", Sample_Name, ignore.case = TRUE),
     #^removes dup, ccv, ccb, standards
     !is.na(Sample_Name),                                         # Remove NA
     !grepl("^\\d+$", Sample_Name),                               # removes all numbers
     !grepl("^\\d{1,2}/\\d{1,2}/\\d{2,4}", Sample_Name)) %>%      # removes all date/time
  mutate(`Spike?` = if_else(                                      # adds duplicate column
     grepl("Auto Spike", Sample_Name, ignore.case = TRUE),        # keeps sample ID if there
     lag(Sample_Name),                                            # get previous row's SampleID
     Sample_Name)) %>%                                            # keeps sample ID if not duplicate
  group_by(`Spike?`) %>%                                          # groups by duplicate
  filter(n() > 1) %>%                                             # filters anything that appears more than once
  ungroup()  %>%
  transmute(
    Pair_ID = `Spike?`,
    Sample_Name,
    Conc,
    Type = if_else(str_detect(Sample_Name, "Auto Spike"), "Auto_Spike", "Original"))
 
df_PO4_spk <- df_all_cor %>%
  filter(Test == "o-PHOS 0.3") %>%
  filter(
     !grepl("CCV|CCB|Standard|Duplicate", Sample_Name, ignore.case = TRUE),
     #^removes dup, ccv, ccb, standards
     !is.na(Sample_Name),                                         # Remove NA
     !grepl("^\\d+$", Sample_Name),                               # removes all numbers
     !grepl("^\\d{1,2}/\\d{1,2}/\\d{2,4}", Sample_Name)) %>%      # removes all date/time
   mutate(`Spike?` = if_else(                                     # adds duplicate column
     grepl("Auto Spike", Sample_Name, ignore.case = TRUE),        # keeps sample ID if there
     lag(Sample_Name),                                            # get previous row's SampleID
     Sample_Name)) %>%                                            # keeps sample ID if not duplicate
  group_by(`Spike?`) %>%                                          # groups by duplicate
  filter(n() > 1) %>%                                             # filters anything that appears more than once
  ungroup()  %>%
  transmute(
    Pair_ID = `Spike?`,
    Sample_Name,
    Conc,
    Type = if_else(str_detect(Sample_Name, "Auto Spike"), "Auto_Spike", "Original"))
 

#checking and flagging against the expected spike conc
df_spk_NOx_chk <- df_NOx_spk %>%
  select(Pair_ID, Conc, Type) %>%
  pivot_wider(
    names_from = Type,
    values_from = Conc,
    values_fn = mean,  # in case there are duplicates
    names_prefix = "" ) %>%
  rename(
    Spike_Conc = Auto_Spike,
    OG_Conc = Original) %>%
  filter(!is.na(Spike_Conc), !is.na(OG_Conc)) %>%
  rowwise() %>%# keep only rows with both
   mutate(
    Exp_Conc = OG_Conc + NOx_Spk,
    Mean_Conc = mean(c(Spike_Conc, Exp_Conc), na.rm = TRUE),
    Pct_Diff = abs(Spike_Conc - Exp_Conc) / Mean_Conc * 100,
    SD_Conc = sd(c(Spike_Conc, Exp_Conc)),
    CV = (SD_Conc / Mean_Conc) * 100,
    Spike_diff_flag = ifelse(CV < 50, "YES", "NO, check"),
    Test = "Vanadium NOx") %>%
    ungroup()
  
df_spk_NH3_chk <- df_NH3_spk %>%
  select(Pair_ID, Conc, Type) %>%
  pivot_wider(
    names_from = Type,
    values_from = Conc,
    values_fn = mean,  # in case there are duplicates
    names_prefix = "" ) %>%
  rename(
    Spike_Conc = Auto_Spike,
    OG_Conc = Original) %>%
  filter(!is.na(Spike_Conc), !is.na(OG_Conc)) %>%
  rowwise() %>%# keep only rows with both
   mutate(
    Exp_Conc = OG_Conc + NH3_Spk,
    Mean_Conc = mean(c(Spike_Conc, Exp_Conc), na.rm = TRUE),
    Pct_Diff = abs(Spike_Conc - Exp_Conc) / Mean_Conc * 100,
    SD_Conc = sd(c(Spike_Conc, Exp_Conc)),
    CV = (SD_Conc / Mean_Conc) * 100,
    Spike_diff_flag = ifelse(CV < 50, "YES", "NO, check"),
    Test = "Ammonia 2") %>%
    ungroup()

df_spk_PO4_chk <- df_PO4_spk %>%
  select(Pair_ID, Conc, Type) %>%
  pivot_wider(
    names_from = Type,
    values_from = Conc,
    values_fn = mean,  # in case there are duplicates
    names_prefix = "" ) %>%
  rename(
    Spike_Conc = Auto_Spike,
    OG_Conc = Original) %>%
  filter(!is.na(Spike_Conc), !is.na(OG_Conc)) %>%
  rowwise() %>%# keep only rows with both
   mutate(
    Exp_Conc = OG_Conc + PO4_Spk,
    Mean_Conc = mean(c(Spike_Conc, Exp_Conc), na.rm = TRUE),
    Pct_Diff = abs(Spike_Conc - Exp_Conc) / Mean_Conc * 100,
    SD_Conc = sd(c(Spike_Conc, Exp_Conc)),
    CV = (SD_Conc / Mean_Conc) * 100,
    Spike_diff_flag = ifelse(CV < 50, "YES", "NO, check"),
    Test = "o-PHOS 0.3") %>%
    ungroup()


# Combining Auto Spike data frames
df_spk_combo <- bind_rows(df_spk_NOx_chk, df_spk_NH3_chk, df_spk_PO4_chk)

#add column for test ^^ aand then combine


#calculate the percent of check standards that are within the range based on the flag
NOx_spk_percent <- (sum(df_spk_NOx_chk$Spike_diff_flag == "YES")/nrow(df_spk_NOx_chk))*100
NH3_spk_percent <- (sum(df_spk_NH3_chk$Spike_diff_flag == "YES")/nrow(df_spk_NH3_chk))*100
PO4_spk_percent <- (sum(df_spk_PO4_chk$Spike_diff_flag == "YES")/nrow(df_spk_PO4_chk))*100
 

#spk flag report out
ifelse(NOx_spk_percent >= chks_flag, 
       ">60% of Spikes have a CV <50% - PROCEED",
       "<60% of Carbon Spikes have a CV <50% - REASSESS")
ifelse(NH3_spk_percent >= chks_flag, 
       ">60% of Spikes have a CV <50% - PROCEED",
       "<60% of Carbon Spikes have a CV <50% - REASSESS")
ifelse(PO4_spk_percent >= chks_flag, 
       ">60% of Spikes have a CV <50% - PROCEED",
       "<60% of Carbon Spikes have a CV <50% - REASSESS")
 

#plot spikes output as a bar graph to easily check - want any over 10% to be red need to work on this 
NOx_spk_plot <- ggplot(data =df_spk_NOx_chk, aes(x =Pair_ID, y =CV, fill=Spike_diff_flag)) +
        geom_bar(stat = 'identity') + 
        theme_classic() + 
        labs(x= "Sample ID", y="NOx N (mg/L)", title = "NOx Auto Spike CV") + 
        scale_fill_manual(values = c("YES" = "darkcyan", "NO, check" = "darkred")) +
        theme(legend.position="none") + 
        geom_hline(yintercept=50, linetype="dashed", 
            color = "black", size=1)  +
        guides(fill=guide_legend(title="CV Between Spks <50%"))+
        theme(axis.text.x = element_text(angle = 90, hjust = 0.5))

NH3_spk_plot <- ggplot(data = df_spk_NH3_chk, aes(x =Pair_ID, y =CV, fill=Spike_diff_flag)) +
        geom_bar(stat = 'identity') + 
        theme_classic() + 
        labs(x= "Sample ID", y="NH3 N(mg/L)", title = "NH3 Auto Spike CV") + 
        scale_fill_manual(values = c("YES" = "darkcyan", "NO, check" = "darkred")) +
        theme(legend.position="none")  + 
        geom_hline(yintercept=50, linetype="dashed", 
            color = "black", size=1)  +
        guides(fill=guide_legend(title="CV Between Spks <50%"))+
        theme(axis.text.x = element_text(angle = 90, hjust = 0.5))

PO4_spk_plot <- ggplot(data =df_spk_PO4_chk, aes(x =Pair_ID, y =CV, fill=Spike_diff_flag)) +
       geom_bar(stat = 'identity') + 
       theme_classic() + 
        labs(x= "Sample ID", y="PO4 P(mg/L)", title = "PO4 Auto Spike CV") + 
       scale_fill_manual(values = c("YES" = "darkcyan", "NO, check" = "darkred")) +
       theme(legend.position="none")  + 
       geom_hline(yintercept=50, linetype="dashed", 
            color = "black", size=1)  +
        guides(fill=guide_legend(title="CV Between Spks <50%"))+
        theme(axis.text.x = element_text(angle = 90, hjust = 0.5))
 

Spk_Plots <- ggarrange(
  NOx_spk_plot, 
  NH3_spk_plot, 
  PO4_spk_plot,   # (you had NH3 twice!)
  nrow = 1, 
  ncol = 3,
  common.legend = TRUE,
  legend = "bottom")
print(Spk_Plots)


#write out a flag to the sample dataframe if more than 60% of the dups have CVs out of range
if (NOx_spk_percent <= chks_flag) {
    df_all_cor$NOx_flag <- ifelse(
    df_all_cor$NOx_flag != "",
    paste0(df_all_cor$NOx_flag, "; NOx spikes out of range"),
    "NOx spikes out of range"
  )
}

if (NH3_spk_percent <= chks_flag) {  
    df_all_cor$NH3_flag <- ifelse(
    df_all_cor$NH3_flag != "",
    paste0(df_all_cor$NH3_flag, "; NH3 spikes out of range"),
    "NH3 spikes out of range"
  )
}

if (PO4_spk_percent <= chks_flag) {  
    df_all_cor$PO4_flag <- ifelse(
    df_all_cor$PO4_flag != "",
    paste0(df_all_cor$PO4_flag, "; PO4 spikes out of range"),
    "PO4 spikes out of range"
  )
}


```

\newpage

## Matrix Effects
```{r Analyze Matrix Effects, echo=FALSE}

df_matrix <- df_spk_combo%>%
  filter(str_detect(Pair_ID, "Abs_Chk")) 

df_matrix_NOx <- df_matrix %>%
  filter(str_detect(Test, "Vanadium")) 
  ifelse(
  all(df_matrix_NOx$Spike_diff_flag == "YES"),
  "NO NOx Matrix Effect, PROCEED",
  ">20% CV in ASW NOx matrix effect checks - REASSESS"
)
  
df_matrix_NH3 <- df_matrix %>%
  filter(str_detect(Test, "Ammonia")) 
  ifelse(
  all(df_matrix_NH3$Spike_diff_flag == "YES"),
  "NO NH3 Matrix Effect, PROCEED",
  ">20% CV in ASW NH3 matrix effect checks - REASSESS"
)
  
df_matrix_PO4 <- df_matrix %>%
  filter(str_detect(Test, "PHOS")) 
  ifelse(
  all(df_matrix_PO4$Spike_diff_flag == "YES"),
  "NO PO4 Matrix Effect, PROCEED",
  ">20% CV in ASW PO4 matrix effect checks - REASSESS"
)



#write out a flag to the sample dataframe if more than 60% of the dups have CVs out of range
if (any(df_matrix$Spike_diff_flag[df_matrix$Test == "Vanadium NOx"] != "YES")) {
  
    df_all_cor$NOx_flag <- ifelse(
    df_all_cor$NOx_flag != "",
    paste0(df_all_cor$NOx_flag, "; NOx matrix check out of range"),
    "NOx matrix check out of range"
  )

}

if (any(df_matrix$Spike_diff_flag[df_matrix$Test == "Ammonia 2"] != "YES")) {
  
    df_all_cor$NH3_flag <- ifelse(
    df_all_cor$NH3_flag != "",
    paste0(df_all_cor$NH3_flag, "; NH3 matrix check out of range"),
    "NH3 matrix check out of range"
  )

}

if (any(df_matrix$Spike_diff_flag[df_matrix$Test == "o-PHOS 0.3"] != "YES")) {
  
    df_all_cor$PO4_flag <- ifelse(
    df_all_cor$PO4_flag != "",
    paste0(df_all_cor$PO4_flag, "; PO4 matrix check out of range"),
    "PO4 matrix check out of range"
  )

}

```

## Unit Converted Data Column Added (mg/L to uM )
```{r Add unit conversion, include=FALSE}

#Pull out samples 
samples <- df_all_cor %>%  
  filter(str_detect(Sample_Name, c("GCW|GWI|MSM|SWH")))     


#Convert values based on the Test ID 
samples <- samples %>%
  mutate(
    Conc_uM = case_when(
      Test == "Vanadium NOx" ~ (((as.numeric(samples$Conc))/Con1)/N_mw)*Con2,
      Test == "Ammonia 2" ~ (((as.numeric(samples$Conc))/Con1)/N_mw)*Con2,
      Test == "o-PHOS 0.3" ~ (((as.numeric(samples$Conc))/Con1)/P_mw)*Con2,
      TRUE ~ as.numeric(NA)  # fallback in case of unexpected value
    ),
    # Replace negatives with 0 in 'value' and 'value_converted'
    Conc = pmax(Conc, 0),
    Conc_uM = pmax(Conc_uM, 0)
  )

head(samples)

```

## Sample Flagging - Within range of standard curve
```{r Sample Flagging, echo=FALSE}

cat("Sample Flagging")

#Flagging data if the concentration is outside the standards range 
samples_flagged <- samples %>%
  mutate(
    Conc_flag = case_when(
      Test == "Vanadium NOx" & Conc < NOx_dl ~ "bdl",
      Test == "Vanadium NOx" & Conc > NOx_top    ~ "adl",
      Test == "Vanadium NOx"               ~ "Within_Range",
      
      Test == "Ammonia 2" & Conc < NH3_dl ~ "bdl",
      Test == "Ammonia 2" & Conc > NH3_top    ~ "adl",
      Test == "Ammonia 2"                ~ "Within_Range",
      
      Test == "o-PHOS 0.3" & Conc < PO4_dl  ~ "bdl",
      Test == "o-PHOS 0.3" & Conc > PO4_top   ~ "adl",
      Test == "o-PHOS 0.3"                ~ "Within_Range",
      
      TRUE ~ NA_character_  # fallback for unexpected values
    )
  )

```
## Create metadata columns to match other outputs
```{r check sample ids with metadata, echo=FALSE}

cat("Create Metadata")

#need to remove SW from the sample IDs because not used any other time and makes it difficult 
#samples_flagged <- samples_flagged %>%
#  mutate(
#    Sample_Name = str_remove(Sample_Name, fixed("_SW"))
#  )

#Plot samples to get a first look at concentrations (sanity check)
IDs <- data.frame(do.call('rbind', strsplit(as.character(samples_flagged$Sample_Name),'_',fixed=TRUE)))
colnames(IDs) <- c("Experiment" , "Site_Code","Sample_Type", "Sample_ID","Extra") # "Sample_Date", "Time")
#head(IDs)

#rejoin them to the dataframe
dat_flagged_id <- cbind(IDs, samples_flagged)

#create important columns from the sample_name 
df_all_clean <- dat_flagged_id %>%
  mutate(Sample_Date = NA_character_, 
         Time = NA_character_) %>%
  mutate(
    Sample_Type = if_else(
      str_detect(Sample_Name, regex("T\\d+", ignore_case = TRUE)),
      "SW",
      "Endmember"),
    Paired = if_else(
      str_detect(Sample_Name, "Pair"),
      "Paired",
      NA_character_)) %>%
  filter(!str_detect(Sample_Name, regex("_dup", ignore_case = TRUE))) #remove duplicates


```


\newpage

## Visualize Data
```{r Visualize Data, echo=FALSE}
cat("Visualize Data")

### Nitrite + Nitrate 

NOx_forplot <- df_all_clean %>%
  filter(Test == "Vanadium NOx")

#group the data for plotting
NOx_forplot <- NOx_forplot %>%
  group_by(Site_Code) %>%
  mutate(row_num = factor(row_number())) %>%  # create row_num as factor per group
  ungroup()

viz_NOx_plot <-  ggplot(data = NOx_forplot, aes(x = factor(row_num), y = Conc, fill=Sample_Type)) +
       geom_bar(stat = "identity", position = position_dodge2(preserve = "single"), 
                 color="black") +
        theme_classic() + 
        labs(x= " ", y="NOx (mg/L)", title="Porewater NOx") + 
          theme(legend.position = "right") +
          scale_x_discrete(drop = TRUE)+
        theme(axis.text.x = element_text(angle = 90, hjust = 0.5))

### Ammonia 

NH3_forplot <- df_all_clean %>%
  filter(Test == "Ammonia 2")

#group the data for plotting
NH3_forplot <- NH3_forplot %>%
  group_by(Site_Code) %>%
  mutate(row_num = factor(row_number())) %>%  # create row_num as factor per group
  ungroup()

viz_NH3_plot <- ggplot(data = NH3_forplot, aes(x = factor(row_num), y = Conc, fill=Sample_Type))  +
       geom_bar(stat = "identity", position = position_dodge2(preserve = "single"), 
                 color="black") + 
        theme_classic() + 
        labs(x= " ", y="NH3 (mg/L)", title="Porewater NH3") + 
          theme(legend.position = "right") +
          scale_x_discrete(drop = TRUE)+
        theme(axis.text.x = element_text(angle = 90, hjust = 0.5))

### Phosphate 

PO4_forplot <- df_all_clean %>%
  filter(Test == "o-PHOS 0.3")

#group the data for plotting
PO4_forplot <- PO4_forplot %>%
  group_by(Site_Code) %>%
  mutate(row_num = factor(row_number())) %>%  # create row_num as factor per group
  ungroup()

viz_PO4_plot <- ggplot(data = PO4_forplot,aes(x = factor(row_num), y = Conc, fill=Sample_Type))  +
       geom_bar(stat = "identity", position = position_dodge2(preserve = "single"), 
                 color="black") + 
        theme_classic() + 
        labs(x= " ", y="PO4 (mg/L)", title="Porewater PO4") + 
          theme(legend.position = "right") +
          scale_x_discrete(drop = TRUE)+
        theme(axis.text.x = element_text(angle = 90, hjust = 0.5))


print(viz_NOx_plot)
print(viz_NH3_plot) 
print(viz_PO4_plot)

```

## Export Processed Data
```{r Export Processed Data, include=FALSE}

cat("Export Processed Data")

#pivot the data set wider to make it wide format 
final_data1 <- df_all_clean %>%
  pivot_wider(
    id_cols = Sample_Name,
    names_from = Test,
    values_from = Conc,
    names_glue = "{Test}_Conc"
  )

final_data2 <- df_all_clean %>%
  pivot_wider(
    id_cols = Sample_Name,
    names_from = Test,
    values_from = Conc_uM,
    names_glue = "{Test}_Conc_uM"
  )

final_data3 <- df_all_clean %>%
  pivot_wider(
    id_cols = Sample_Name,
    names_from = Test,
    values_from = Conc_flag,
    names_glue = "{Test}_Conc_flag"
  )

#take out only the columns we want to merge 
df_all_clean_cols <- df_all_clean %>%
  select(Experiment, Site_Code, Sample_Type, Sample_ID,Sample_Date, Time,
         Sample_Name, 
         NOx_flag, NH3_flag, PO4_flag)

df_all_clean_cols_one_row <- df_all_clean_cols %>%
  group_by(Sample_Name) %>%
  slice(1) %>%  # or use summarise() if you want to aggregate
  ungroup()

#merge these together
data_list <- list(df_all_clean_cols_one_row, final_data1, final_data2, final_data3)

final_data4 <- reduce(data_list, full_join, by = c("Sample_Name"))


#Add project information 
final_data_labeled <- final_data4 %>% 
  mutate(
    Project = "COMPASS: Synoptic",   # new column with same value on every row
    Region = "CB",
    Run_notes = run_notes, 
    Analysis_rundate = print(run_date)# new column with notes about the run
  ) 

#Prepare data to be exported 
final_data <- final_data_labeled %>%
    rename(
    sample_name = Sample_Name, 
    
    NOx_Conc_mgL = `Vanadium NOx_Conc`,
    NOx_Conc_uM = `Vanadium NOx_Conc_uM`,
    NOx_Conc_Flag = `Vanadium NOx_Conc_flag`,
    NOx_QAQC_Flag = NOx_flag,
    
    NH3_Conc_mgL = `Ammonia 2_Conc`,
    NH3_Conc_uM = `Ammonia 2_Conc_uM`,
    NH3_Conc_Flag =`Ammonia 2_Conc_flag`,
    NH3_QAQC_Flag = NH3_flag,
    
    PO4_Conc_mgL = `o-PHOS 0.3_Conc`,
    PO4_Conc_uM = `o-PHOS 0.3_Conc_uM`,
    PO4_Conc_Flag =`o-PHOS 0.3_Conc_flag`,
    PO4_QAQC_Flag = PO4_flag
    
    # add more rename pairs as needed
  ) %>%
  select(Project, Region, Experiment, Site_Code, Sample_Type, 
         Sample_Date, Time, 
         sample_name, 
         NOx_Conc_mgL, NOx_Conc_uM, NOx_Conc_Flag, NOx_QAQC_Flag,
         NH3_Conc_mgL, NH3_Conc_uM, NH3_Conc_Flag, NH3_QAQC_Flag,
         PO4_Conc_mgL, PO4_Conc_uM, PO4_Conc_Flag, PO4_QAQC_Flag,
         Analysis_rundate,  Run_notes)


#Write out data frame 
  write.csv(final_data, final_path)
  

```



#end