---
title: "Synoptic CB: Lateral Transport Surveys SO4/Cl"
author: "GCW Survey Samples"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
    number_sections: true

output_dir: "To Be Reviewed/PDF"
---

\newpage

##Add Required Packages
```{r packages, include=FALSE}

#Packages that are required 
lapply(c(
  "dplyr", "ggplot2", "ggpubr", "stringr",
  "purrr", "tidyverse", "here", "broom", "tibble",
  "googledrive", "googlesheets4", "data.table", 
  "matrixStats", "gridExtra", "grid", "tidyverse", "knitr"), 
  library, character.only = TRUE)

```


## Run Information
```{r Run Information, echo=TRUE, message=FALSE, warning=FALSE}

###### Run information - PLEASE CHANGE
  Date_Run = "2025-10-03"  #Date that instrument was run
  Run_by = "Zoe Read"  #Instrument user 
  Script_run_by = "Stephanie Wilson" #Code user 
  run_notes = " " #any notes from the run

###### File Names - PLEASE CHANGE 
#file path and name for raw summary data file 
  raw_file_name_cl = c("Raw_GCW_Data/COMPASS_2024_GCW_Lateral_Transport_Survey_Cl.txt")
  raw_file_name_so4 = "Raw_GCW_Data/COMPASS_2024_GCW_Lateral_Transport_Survey_SO4.txt"

#file path and name of processed data file 
  processed_file_name = "Processed_GCW_Data/GCW_SO4_Cl_processed.csv" 

#metadata csv 
  Raw_Metadata = "Raw_GCW_Data/COMPASS_SynopticCB_LatT_GCW_Discrete_Metadata.csv"

#qaqc log file path for this year 
  Log_path = "Raw_GCW_Data/COMPASS_Synoptic_Cl_SO4_QAQClog_2024.csv"

```


##Set Up Code - constants and QAQC cutoffs
```{r Constants and QAQC cutoffs, include=FALSE}

#Link to the protocol used for analysis 
  #steph will add this soon 

#Coefficients / constants that are needed for calculations 
  cl_mw <- 35.45     #molecular weight of Chloride, g/mol
  s_mw <- 32.06      #molecular weight of sulfur, g/mol
  Con1 <- 1000000    #conversion factor value for spike volumes (uL -> L)

#Flag cutoffs
  r2_cutoff = 0.98            #this is the level below which we want to rerun or consider a curve 
  chk_flag_std_s = 10         #this is the maximum cv allowed for sulfate check standards
  chk_flag_std_cl = 5         #this is the maximum cv allowed for chloride check standards
  chk_flag_std_perc = 15      #this is the maximum perc diff allowed for check standards
  chk_flag_dups = 10          #this is the maximum cv allowed for duplicates
  high_recovery_cutoff = 120  #this is the maximum percent recovery of SO4 allowed in spiked samples
  low_recovery_cutoff = 80    #this is the minimum percent recovery of SO4 allowed in spiked samples
  chks_flag = 80              #if less than this percent of samples pass a check, a flag is added

#Standard concentrations - Update if running different standard curve:  
  standards <- tibble(
    sample_ID = c("Standard 1", "Standard 2", "Standard 3", "Standard 4", "Standard 5"),
    SO4_std_conc = c(0.5, 1.0, 2.0, 10, 20),  #ug/mL
    Cl_std_conc = c(5, 10, 20, 100, 200))     #ug/mL

#Spike concentration calc 
  #spike for these samples was 10uL of the 250 µg/mL standard
  spk_std <- (250/s_mw)         # mM of SO4 calculated from 250 ug/mL SO4 spike solution
  spkvol <- 10                  # uL volume of spike added
  spkvol <- spkvol/Con1         # L volume of spike added
  spk_Conc <- (spk_std)*spkvol  # mmoles of SO4 added to each spiked sample
  SampleVol <- 1500             # total volume of diluted sample in Dionex vial in uL
   
#Top standard Concentrations- Update if running different standard curve: 
   top_std_cl = 200   #ug/mL
   top_std_so4 = 20   #ug/mL

#Set time zone 
  common_tz = "Etc/GMT+5"
  Sys.setenv(TZ = "America/New_York")


```

##Read in metadata and create similar sample IDs for matching to samples 
```{r pull in metadata for later, include=FALSE}

#read in the raw metadata file 
raw_metadata <- read.csv(Raw_Metadata)

#create project column in metadata 
metadata <- raw_metadata %>%
  mutate(Project = "LatT") %>%
   mutate(sample_id = str_replace_all(sample_id, "-", "_"))

#Create NUTR IDs from what was collected for comparison later
metadata <- metadata %>%
  mutate(Cl_SO4_ID =   paste(Project,
                     site,
                     samply_type,
                     sample_id,
                     sep = "_"))

#Take out the columns and rows that are not relevant
dionex_metadata <- metadata %>%
  select(Cl_SO4_ID, site, samply_type, sample_id, date_sampled, time_sampled_est) %>%        
  # only keep specific columns
  filter(!is.na(Cl_SO4_ID) & Cl_SO4_ID != "")  # remove missing/blank NUTR_ID rows

head(dionex_metadata)

```

##Import Sample Data - need to change LTS to LatT and remove the date 
```{r import data, include=FALSE}

## Read in raw data file from Dionex - copied and saved as a txt
#Sulfate
Sdat <- read.table(raw_file_name_so4, sep='\t' , header=T, skip=3)

Sdat_clean <- Sdat %>%
  select(
    sample_name = X.1,
    sample_ID = X.1,
    sample_type = X.2,
    SO4_ppm = IC.SO4.1, 
    SO4_area = IC.SO4.3
  ) %>%
  group_by(sample_name) %>%
   mutate(sample_name = if_else(
    sample_name %in% c("Lab Blank", "Standard 1", "Standard 2", "Standard 3", "Standard 4", "Standard 5"),
    paste0(sample_name, "_", row_number()),
    sample_name
  )) %>%
  ungroup()
  #head(Sdat_clean)

#Chloride
Cldat  <- read.table(raw_file_name_cl, sep='\t' , header=T, skip=3)

Cldat_clean <- Cldat %>%
  select(
    sample_name = X.1,
    sample_ID = X.1,
    sample_type = X.2,
    Cl_ppm = IC.Cl.1,
    Cl_area = IC.Cl.3
  ) %>%
  group_by(sample_name) %>%
   mutate(sample_name = if_else(
    sample_name %in% c("Lab Blank", "Standard 1", "Standard 2", "Standard 3", "Standard 4", "Standard 5"),
    paste0(sample_name, "_", row_number()),
    sample_name
  )) %>%
  ungroup()
  #head(Cldat_clean)


## Pull Cl and SO4 data  together: 
all_dat_merge <- inner_join(Sdat_clean, Cldat_clean, by = c("sample_name", "sample_ID", "sample_type"))

#Remove any lines that have no sample ID, make n.a. into NAs,
  #if there are NAs or zeroes in the SO4 or Cl columns, make them zeros because that means there was no peak detected
all_dat1 <- all_dat_merge %>%
  filter(!is.na(sample_ID) & sample_ID != "") %>%
  mutate(across(everything(), ~ na_if(.x, "n.a."))) %>%
  mutate(across(c(SO4_ppm, Cl_ppm), as.numeric), 
         across(c(SO4_area, Cl_area), as.numeric)) %>%
  mutate(across(c(SO4_ppm, Cl_ppm), ~ replace_na(.x, 0)), 
         across(c(SO4_area, Cl_area), ~ replace_na(.x, 0))) %>%
  mutate(across(c(SO4_ppm, Cl_ppm), ~ replace(.x, .x<0, 0)), 
         across(c(SO4_area, Cl_area), ~ replace(.x, .x<0, 0)))




#deal with weird way the samples are named here 
all_dat2 <- all_dat1 %>%
  mutate(
    sample_ID = sample_ID %>%
      str_replace("^\\d+_", "") %>% 
      str_replace("LTS", "LatT") %>%             # Replace LTS at the beginning with LatT
      str_remove("\\d{8}")     %>%  # Remove any 8-digit number (date)
    str_remove("_\\d{4}(?=_|$)")
  ) %>%
  mutate(
    sample_ID = sample_ID %>%
      str_replace("PAIRED", "Pair") %>%
      str_replace("DUP", "dup") %>%
      str_replace("SPK", "spk") %>%
      str_replace("_LOW_", "_") %>%
      str_replace("_GW_", "_") %>%
      str_replace("CBSYN_WC", "GW_WC_1") %>%
      str_replace("ESTUARY_", "EST") %>%
      str_replace("EST1", "EST_1") %>%
      str_replace("EST2", "EST_2") %>%
      str_replace("EST3", "EST_3") %>%
      str_replace("DOCK-2", "EST_5") %>%
      str_replace("DOCK", "EST_4") %>%
      str_replace("FW-1_UP-1", "GW_UP_1") %>%
      str_replace("FW-1_UP-2", "GW_UP_2") %>%
      str_replace("WC_1-2", "WC_2") %>%
      str_replace("_GW2_WE1", "GW_WE_1") %>%
      str_replace("_GW2_WE2", "GW_WE_2") %>%
      str_replace("GW3", "GW_WE_3") %>%
      str_replace("GW4", "GW_WE_4") )%>%
  mutate(sample_ID = sample_ID %>% str_replace("__", "_"))


#rename the two rows that are Paired samples T75 and T76 
all_dat <- all_dat2 %>%
  mutate(sample_ID = case_when(
    sample_name == "122_LTS_GCW_SW_20240718_PAIRED_1300" ~ "LatT_GCW_SW_T75_Pair",
    sample_name == "122_LTS_GCW_SW_20240718_PAIRED_1300_DUP" ~ "LatT_GCW_SW_T75_Pair_dup",
    sample_name == "123_LTS_GCW_SW_20240718_PAIRED_1400" ~ "LatT_GCW_SW_T76_Pair",
    sample_name == "123_LTS_GCW_SW_20240718_PAIRED_1400_SPK" ~ "LatT_GCW_SW_T76_Pair_spk",
    sample_name == "121_LTS_GCW_SW_20240718_SW_1200" ~ "LatT_GCW_SW_T74",
    TRUE ~ sample_ID  # Keep original if no match
  ))

head(all_dat)

```

## Assess Standard Curves
```{r Assess Standards, echo=FALSE, message=FALSE, warning = FALSE, fig.height = 4}

# Filter standards
stds <- all_dat %>%
  filter(grepl("Calibration Standard", sample_type)) %>%
  mutate(run_date = Date_Run)

#calculate slope and r2 of cal curves
#Cl curve
lm_results_cl <- stds %>%
  group_by(run_date) %>%
  do({
    model = lm(Cl_area ~ Cl_ppm, data = .)
    tidy_model = tidy(model)             # coefficients
    glance_model = glance(model)         # model metrics like R²
    tibble(
      slope = tidy_model$estimate[2],    # coefficient for standard_C_ppm
      intercept = tidy_model$estimate[1],
      r2 = glance_model$adj.r.squared
    )
  }) %>%
  mutate(
    analyte = "Cl", 
    curve = "Chloride (mg/L)"
  )

#SO4 curve
lm_results_s <- stds %>%
  group_by(run_date) %>%
  do({
    model = lm(SO4_area ~ SO4_ppm, data = .)
    tidy_model = tidy(model)             # coefficients
    glance_model = glance(model)         # model metrics like R²
    tibble(
      slope = tidy_model$estimate[2],    # coefficient for standard_C_ppm
      intercept = tidy_model$estimate[1],
      r2 = glance_model$adj.r.squared
    )
  }) %>%
  mutate(
    analyte = "SO4", 
    curve = "SO4 (mg/L)"
  )

#put the together in one dataframe to later add to log 
Slopes <- rbind(lm_results_cl, lm_results_s)

#store the r2's so they plot on the curve graphs
r2_labels_cl <- stds %>%
  group_by(run_date) %>%
  summarise(
    x_pos = max(Cl_ppm, na.rm = TRUE) * 0.8,
    y_pos = max(Cl_area, na.rm = TRUE),
    r_squared = round(summary(lm(Cl_area ~ Cl_ppm))$adj.r.squared, 4),
    .groups = "drop"
  )

r2_labels_so4 <- stds %>%
  group_by(run_date) %>%
  summarise(
    x_pos = max(SO4_ppm, na.rm = TRUE) * 0.8,
    y_pos = max(SO4_area, na.rm = TRUE),
    r_squared = round(summary(lm(SO4_area ~ SO4_ppm))$adj.r.squared, 4),
    .groups = "drop"
  )


##Plot standard Curve or Curves 
#Cl Curve
Cl_stds_plot <- ggplot(stds, aes(x = Cl_ppm, y = Cl_area)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  facet_wrap(~ run_date) +
  geom_text(
    data = r2_labels_cl,
    aes(x = x_pos, y = y_pos, label = paste0("R² = ", r_squared)),
    inherit.aes = FALSE,
    hjust = 1, vjust = 1,
    size = 4
  ) +
  labs(
    title = "Chloride Std Curve",
    x = "Cl Standard Concentration (ppm)",
    y = "Peak Area"
  ) +
  theme_bw()

Cl_stds_plot

#SO4 Curve
SO4_stds_plot <- ggplot(stds, aes(x = SO4_ppm, y = SO4_area)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE, color = "purple") +
  facet_wrap(~ run_date) +
    geom_text(
    data = r2_labels_so4,
    aes(x = x_pos, y = y_pos, label = paste0("R² = ", r_squared)),
    inherit.aes = FALSE,
    hjust = 1, vjust = 1,
    size = 4
  ) +
  labs(
    title = "Sulfate Std Curve",
    x = "SO4 Standard Concentration (ppm)",
    y = "Peak Area"
  ) +
  theme_bw()

SO4_stds_plot

#compare slopes to previous runs (from log) in order to assess drift 
#check for the a slope QAQC file, if there is not one, make one 
if (file.exists(Log_path)) {
  # If it exists, read it back into R
  log <- read.csv(Log_path)
  print("QAQC log file exists and has been read into the code.")
  } else {
  # If it does not exist, create the CSV file
  log <- as.data.frame(matrix(ncol = 7, nrow = 0))
  colnames(log) <- c( "X", "r2", "analyte", "curve", "run_date", "slope", "intercept")
  
  # Write add_log to CSV
  write.csv(log, file = Log_path, row.names = FALSE)
  print("QAQC log file does not exist. It has been created.")
  }

log <- log[ ,-c(1)]

#make sure they both have dates in Date format
log$run_date <- as.Date(log$run_date, format = "%Y-%m-%d")
log$analyte <- as.character(log$analyte)
log$curve <- as.character(log$curve)
Slopes$run_date <- as.Date(Slopes$run_date)

# Filter to only rows in Slopes that are NOT already in log (by run_date + analyte)
new_rows <- anti_join(Slopes, log, by = c("run_date", "analyte"))

# Append the new, non-duplicate rows to log
log <- bind_rows(log, new_rows)

#plot the current slops with the previous slopes 
Slopes_chk <- ggplot(log, aes(run_date, slope, col=curve)) +
  geom_point(size=4) + 
  geom_line() + 
  theme_bw() + labs(title="Slope Drift Assessment", x="Run Date", y="Slope") +
  scale_color_manual(values=c("blue", "purple"))
Slopes_chk

#write out the log file with the added lines for this run  
write.csv(log, Log_path)

#Grab the highest r2 that is available for this run 
r2_Cl = max(lm_results_cl$r2)
r2_SO4 = max(lm_results_s$r2)

#Write out to the user whether or not the r2 is above the cutoff
  ifelse(r2_Cl <= r2_cutoff, 
         "Cl Curve r2 is below cutoff! - REASSESS", "Cl Curve r2 GOOD")
  ifelse(r2_SO4 <= r2_cutoff, 
         "SO4 Curve r2 is below cutoff! - REASSESS", "SO4 Curve r2 GOOD")
  
#write out a flag to the sample dataframe if the r2 is above the cutoff of 0.98
all_dat <- all_dat %>%
  mutate(
    Cl_QAQC_flag = if (r2_Cl <= r2_cutoff) {
      "Cl r2 low"
    } else {
      ""
    },
    SO4_QAQC_flag = if (r2_SO4 <= r2_cutoff) {
      "SO4 r2 low"
    } else {
      ""
    }
  )

```


## Assess Check Standards 
```{r Check Standards, echo=FALSE, warning = FALSE}

# Pull out check standards
chks_raw <- all_dat %>%
  filter(grepl("Standard", sample_type))%>% 
  mutate(rep = row_number())

#Cl standards
chks_Cl <- chks_raw %>%
  group_by(sample_ID) %>%
  summarise(
    mean_Cl = mean(Cl_ppm, na.rm = TRUE),
    sd_Cl = sd(Cl_ppm, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    cv_Cl = (sd_Cl / mean_Cl),
    flag_Cl = ifelse(cv_Cl < chk_flag_std_cl, "Chloride Check Standard RSD within Range - PROCEED", "Chloride CHECK STANDARD RSD TOO HIGH - REASSESS")
  )

#SO4 standards
chks_S <- chks_raw %>%
  group_by(sample_ID) %>%
  summarise(
    mean_SO4 = mean(SO4_ppm, na.rm = TRUE),
    sd_SO4 = sd(SO4_ppm, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    cv_SO4 = (sd_SO4 / mean_SO4),
    flag_SO4 = ifelse(cv_SO4 < chk_flag_std_s, "Sulfate Check Standard RSD within Range - PROCEED", "Sulfate CHECK STANDARD RSD TOO HIGH - REASSESS")
  )

# View results
head(chks_Cl)
head(chks_S)


#calculate the percent of check standards that have high cv's based on the flag 
cl_chks_percent_cv <- (sum(chks_Cl$flag_Cl == "Chloride Check Standard RSD within Range - PROCEED")/nrow(chks_Cl))*100
so4_chks_percent_cv <- (sum(chks_S$flag_SO4 == "Sulfate Check Standard RSD within Range - PROCEED")/nrow(chks_S))*100

#report out if flags indicate need for rerun
ifelse(cl_chks_percent_cv >= chks_flag, ">80% of Chloride Check Standards have RSD within range - PROCEED",
       "<80% of Chloride Check Standards have RSD within range - REASSESS")
ifelse(so4_chks_percent_cv >= chks_flag,">80% of Sulfate Check Standards have RSD within range - PROCEED",
       "<80% of Sulfate Check Standards have RSD within range - REASSESS")

#write out a flag to the sample dataframe if less than 80% of the check standard RSD's are within range
if (cl_chks_percent_cv <= chks_flag) {
    all_dat$Cl_QAQC_flag <- ifelse(
    all_dat$Cl_QAQC_flag != "",
    paste0(all_dat$Cl_QAQC_flag, "; Cl checks RSD out of range"),
    "Cl checks RSD out of range"
  )
}

if (so4_chks_percent_cv <= chks_flag) {  
    all_dat$SO4_QAQC_flag <- ifelse(
    all_dat$SO4_QAQC_flag != "",
    paste0(all_dat$SO4_QAQC_flag, "; SO4 checks RSD out of range"),
    "SO4 checks RSD out of range"
  )
}





##Add in the expected concentrations
chks_merged <- left_join(chks_raw, standards, by = "sample_ID")

##Order by standard concentration and add rep numbers
chks_merged <- chks_merged[order(chks_merged$SO4_std_conc, chks_merged$Cl_std_conc), ]
chks_merged <- chks_merged %>%
  mutate(rep = row_number())

#calculate percent difference between check standards & expected concentration 
chks_merged$Cl_diff <- (abs(chks_merged$Cl_ppm - chks_merged$Cl_std_conc)/((chks_merged$Cl_ppm + chks_merged$Cl_std_conc)/2)) * 100
chks_merged$Cl_diff_flag <-  ifelse(chks_merged$Cl_diff <= chk_flag_std_perc, 'YES', 'No, rerun')

chks_merged$SO4_diff <- (abs(chks_merged$SO4_ppm - chks_merged$SO4_std_conc)/((chks_merged$SO4_ppm + chks_merged$SO4_std_conc)/2)) * 100
chks_merged$SO4_diff_flag <-  ifelse(chks_merged$SO4_diff <= chk_flag_std_perc, 'YES', 'No, rerun')

# chks_merged[c("sample_ID", "Cl_diff", "Cl_diff_flag", "SO4_diff", "SO4_diff_flag")]


#Plot the check standards vs. the expected concentration 
##Maybe arrange by standard number and add horizontal lines to graphs showing where the expected concentration is? 
custom_y_breaks_Cl <- standards$Cl_std_conc
custom_y_labels_Cl <- standards$sample_ID
cl_chks <-  ggplot(data = chks_merged, aes(x = rep, y = Cl_ppm, fill=Cl_diff_flag)) +
        geom_bar(stat = 'identity') + 
        scale_fill_manual(values = c("YES" = "darkgreen", "No, rerun" = "red")) +
        theme_classic() + labs(x= " ", y="Cl (ppm)", title="Check Stds: Chloride") + 
        theme(legend.position="bottom") +  
        geom_hline(yintercept=standards$Cl_std_conc, linetype="dashed", color = "black", linewidth=1) + 
        scale_y_continuous(breaks = custom_y_breaks_Cl, labels = custom_y_labels_Cl) +
        guides(fill=guide_legend(title="% Difference <10%"))


custom_y_breaks_SO4 <- standards$SO4_std_conc
custom_y_labels_SO4 <- standards$sample_ID
so4_chks <-  ggplot(data = chks_merged, aes(x = rep, y = SO4_ppm, fill=SO4_diff_flag)) +
        geom_bar(stat = 'identity') + 
        scale_fill_manual(values = c("YES" = "darkgreen", "No, rerun" = "red")) +
        theme_classic() + labs(x= " ", y="SO4  (ppm)", title="Check Stds: Sulfate") + 
        theme(legend.position="bottom") + 
        scale_y_continuous(breaks = custom_y_breaks_SO4, labels = custom_y_labels_SO4) +
        geom_hline(yintercept=standards$SO4_std_conc,linetype="dashed",  color = "black", linewidth=1) + 
              guides(fill=guide_legend(title="% Difference <10%"))

ggarrange(cl_chks, so4_chks, nrow=1, ncol=2)

#calculate the percent of check standards that are within the range based on the flag 
cl_chks_percent <- (sum(chks_merged$Cl_diff_flag == "YES")/nrow(chks_merged))*100
so4_chks_percent <- (sum(chks_merged$SO4_diff_flag == "YES")/nrow(chks_merged))*100

#report out if flags indicate need for rerun
ifelse(cl_chks_percent >= chks_flag, ">80% of Chloride Check Standards are within range of expected concentration - PROCEED",
       "<80% of Chloride Check Standards are within range of expected concentration - REASSESS")
ifelse(so4_chks_percent >= chks_flag,">80% of Sulfate Check Standards are within range of expected concentration - PROCEED",
       "<80% of Sulfate Check Standards are within range of expected concentration - REASSESS")

#write out a flag to the sample dataframe if less than 80% of the checks are within range of expected concentration
if (cl_chks_percent <= chks_flag) {
    all_dat$Cl_QAQC_flag <- ifelse(
    all_dat$Cl_QAQC_flag != "",
    paste0(all_dat$Cl_QAQC_flag, "; Cl checks perc diff out of range"),
    "Cl checks perc diff out of range"
  )
}

if (so4_chks_percent <= chks_flag) {  
    all_dat$SO4_QAQC_flag <- ifelse(
    all_dat$SO4_QAQC_flag != "",
    paste0(all_dat$SO4_QAQC_flag, "; SO4 checks perc diff out of range"),
    "SO4 checks perc diff out of range"
  )
}

```

## Assess Blanks 
```{r Check Blanks, echo=FALSE}

#Pull out the blanks from raw file 
blks_raw <- all_dat %>%
  filter(grepl("Lab Blank", sample_ID))

blks_raw <- blks_raw %>% 
  mutate(rep = row_number())

#Check if the blanks are above the lower 25% quantile of your data 
blk_flag_cl <- quantile(all_dat$Cl_ppm, prob=c(.25))   #this gives you the lower 25% quantile of the data 
blks_raw$Cl_diff_flag <-  ifelse(blks_raw$Cl_ppm <= blk_flag_cl, 'YES', 'No, rerun')

blk_flag_so4 <- quantile(all_dat$SO4_ppm, prob=c(.25))   #this gives you the lower 25% quantile of the data 
blks_raw$so4_diff_flag <-  ifelse(blks_raw$SO4_ppm <= blk_flag_so4, 'YES', 'No, rerun')

#calculate the percent of check standards that are within the range based on the flag 
cl_blks_percent <- (sum(blks_raw$Cl_diff_flag == "YES")/nrow(blks_raw))*100
so4_blks_percent <- (sum(blks_raw$so4_diff_flag == "YES")/nrow(blks_raw))*100

#report out if flags indicate need for rerun
ifelse(cl_blks_percent >= chks_flag, ">80% of Chloride Blank concentrations are lower 25% quartile of samples",
       "<80% of Chloride blanks are lower 25% quartile of samples - REASSESS")
ifelse(so4_blks_percent >= chks_flag, ">80% of Sulfate Blank concentrations are lower 25% quartile of samples",
       "<80% of Sulfate blanks are lower 25% quartile of samples - REASSESS")


#Plot the blanks vs. the lower 25% quantile of your data in this run (black line)
cl_blks <-  ggplot(data = blks_raw, aes(x = rep, y = Cl_ppm, fill=Cl_diff_flag)) +
       geom_bar(stat = 'identity') + 
        scale_fill_manual(values = c("YES" = "darkblue", "No, rerun" = "darkgrey")) +
        theme_classic() + labs(x= " ", y="Cl  (mg/L)", title="Blanks: Chloride") + 
        theme(legend.position="bottom") +  geom_hline(yintercept=blk_flag_cl, linetype="dashed", 
                color = "black", linewidth=1)  + 
                guides(fill=guide_legend(title="Blank Conc <25% Quartile Samples"))

so4_blks <-  ggplot(data = blks_raw, aes(x = rep, y = SO4_ppm, fill=so4_diff_flag)) +
       geom_bar(stat = 'identity') + 
        scale_fill_manual(values = c("YES" = "darkblue", "No, rerun" = "darkgrey")) +
        theme_classic() + labs(x= " ", y="SO4  (mg/L)", title="Blanks: Sulfate") + 
        theme(legend.position="bottom") +  geom_hline(yintercept=blk_flag_so4, linetype="dashed", 
                color = "black", linewidth=1)  + 
                guides(fill=guide_legend(title="Blank Conc <25% Quartile Samples"))

ggarrange(cl_blks, so4_blks, nrow=1, ncol=2)

#print out the average blank concentrations 
blk_avg_cl <- mean(blks_raw$Cl_ppm)
cat("Chloride blanks mean ppm:")
print(blk_avg_cl)

blk_avg_so4 <- mean(blks_raw$SO4_ppm)
cat("Sulfate blanks mean ppm:")
print(blk_avg_so4)

#write out a flag to the sample dataframe if more than 80% of the blanks are above the lower 25% quantile of samples
if (cl_blks_percent <= chks_flag) {
  all_dat$Cl_QAQC_flag <- ifelse(
    all_dat$Cl_QAQC_flag != "",
    paste0(all_dat$Cl_QAQC_flag, "; Cl blanks out of range"),
    "Cl blanks out of range"
  )
}

if (so4_blks_percent <= chks_flag) {  
  all_dat$SO4_QAQC_flag <- ifelse(
    all_dat$SO4_QAQC_flag != "",
    paste0(all_dat$SO4_QAQC_flag, "; SO4 blanks out of range"),
    "SO4 blanks out of range"
  )
}

```

## Assess Duplicates 
```{r Check Duplicates, echo=FALSE}

#pull out any rows that have "dup" in the sample_name column
dups <- all_dat %>%  
  select(!c(sample_name, sample_type, SO4_area, Cl_area, Cl_QAQC_flag, SO4_QAQC_flag)) %>%
  filter(str_detect(sample_ID, "dup"))      #have to change this to match data

#create a new dataframe and remove dups from sample dataframe 
dat_raw2 <- all_dat %>%  
  filter(!str_detect(sample_ID, "dup")) %>%  
  select(!c(sample_name, sample_type, SO4_area, Cl_area, Cl_QAQC_flag, SO4_QAQC_flag))

#remove the dup from these IDs so we will have duplicate sample names
dups <- dups %>%
  mutate(sample_ID = gsub("_dup", "", as.character(sample_ID))) %>%
  rename(
    sample_ID = sample_ID,
    SO4_ppm_dup = SO4_ppm, 
    Cl_ppm_dup = Cl_ppm
  )

#merge with the dataframe so we have a column for the conc and the dup
QAdups <- merge(dat_raw2, dups)

#create a dataframe to compare Cl dups 
df2 <- as.data.frame(QAdups$Cl_ppm)
df2$dups <- QAdups$Cl_ppm_dup

#calculate the cv of the duplicates
df2$sds <- apply(df2,1,sd)
df2$mean <- apply(df2, 1, mean)

QAdups$Cl_dups_cv <- (df2$sds/df2$mean) * 100
QAdups$Cl_dups_cv_flag <-  ifelse(QAdups$Cl_dups_cv <chk_flag_dups, 'YES', 'No, rerun')

#create a dataframe to compare SO4 dups 
df3 <- as.data.frame(QAdups$SO4_ppm)
df3$dups <- QAdups$SO4_ppm_dup

#calculate the cv of the duplicates
df3$sds <- apply(df3,1,sd)
df3$mean <- apply(df3, 1, mean)

QAdups$SO4_dups_cv <- (df3$sds/df3$mean) * 100
QAdups$SO4_dups_cv_flag <-  ifelse(QAdups$SO4_dups_cv <chk_flag_dups, 'YES', 'No, rerun')

#Put all the dups together and create row numbers for plotting
QAdups <- QAdups %>%
  mutate(row_num = row_number())
# QAdups

#plot dups output as a bar graph to easily check
Cl_dups <- ggplot(data =QAdups, aes(x =row_num, y =Cl_dups_cv, fill=Cl_dups_cv_flag)) +
       geom_bar(stat = 'identity') + 
        theme_classic() + labs(x= " ", y="CV of Chloride Duplicates") + 
        scale_fill_manual(values = c("YES" = "darkgreen", "No, rerun" = "red")) +
        theme(legend.position="none") +  geom_hline(yintercept=10, linetype="dashed", 
                color = "black", linewidth=1)  + 
              guides(fill=guide_legend(title="CV Between Dups <10%"))


SO4_dups <- ggplot(data =QAdups, aes(x =row_num, y =SO4_dups_cv, fill=SO4_dups_cv_flag)) +
       geom_bar(stat = 'identity') + 
        theme_classic() + labs(x= " ", y="CV of Sulfate Duplicates") + 
          scale_fill_manual(values = c("YES" = "darkgreen", "No, rerun" = "red")) +
        theme(legend.position="none") +  geom_hline(yintercept=10, linetype="dashed", 
                color = "black", linewidth=1) + 
              guides(fill=guide_legend(title="CV Between Dups <10%"))

ggarrange(Cl_dups, SO4_dups,ncol=2, nrow=1)

#Zeros will create NAs in the flag column, so we need to switch those to Yes's 
QAdups <- QAdups %>%
  mutate(Cl_dups_cv_flag = if_else(is.na(Cl_dups_cv), "YES", Cl_dups_cv_flag)) %>%
  mutate(SO4_dups_cv_flag = if_else(is.na(SO4_dups_cv), "YES", SO4_dups_cv_flag))

#calculate the percent of dups that are within the range based on the flag 
cl_dups_percent <- (sum(QAdups$Cl_dups_cv_flag == "YES")/nrow(QAdups))*100
so4_dups_percent <- (sum(QAdups$SO4_dups_cv_flag == "YES")/nrow(QAdups))*100

#report out if the dups are within range
ifelse(cl_dups_percent >= chks_flag, ">80% of Chloride Duplicates have a CV <10% - PROCEED",
       "<80% of Chloride Duplicates have a CV <10% - REASSESS")
ifelse(so4_dups_percent >= chks_flag, ">80% of Sulfate Duplicates have a CV <10% - PROCEED",
       "<80% of Sulfate Duplicates have a CV <10% - REASSESS")

#write out a flag to the sample dataframe if more than 80% of the dups have CVs out of range 
if (cl_dups_percent <= chks_flag) {
    all_dat$Cl_QAQC_flag <- ifelse(
    all_dat$Cl_QAQC_flag != "",
    paste0(all_dat$Cl_QAQC_flag, "; Cl dups cv out of range"),
    "Cl dups cv out of range"
  )
}

if (so4_dups_percent <= chks_flag) {  
    all_dat$SO4_QAQC_flag <- ifelse(
    all_dat$SO4_QAQC_flag != "",
    paste0(all_dat$SO4_QAQC_flag, "; SO4 dups cv out of range"),
    "SO4 dups cv out of range"
  )
}


#Calculate percent difference between duplicates
QAdups$Cl_dups_diff <- ((abs(QAdups$Cl_ppm - QAdups$Cl_ppm_dup))/((QAdups$Cl_ppm + QAdups$Cl_ppm_dup)/2)) * 100
QAdups$Cl_dups_diff_flag <-  ifelse(QAdups$Cl_dups_diff <chk_flag_dups, 'YES', 'No, rerun')

QAdups$SO4_dups_diff <- ((abs(QAdups$SO4_ppm - QAdups$SO4_ppm_dup))/((QAdups$SO4_ppm + QAdups$SO4_ppm_dup)/2)) * 100
QAdups$SO4_dups_diff_flag <-  ifelse(QAdups$SO4_dups_diff <chk_flag_dups, 'YES', 'No, rerun')


#plot dups output as a bar graph to easily check
Cl_dups1 <- ggplot(data =QAdups, aes(x =row_num, y =Cl_dups_diff, fill=Cl_dups_diff_flag)) +
       geom_bar(stat = 'identity') + 
        theme_classic() + labs(x= " ", y="Difference Between Chloride Duplicates (%)") + 
        scale_fill_manual(values = c("YES" = "darkgreen", "No, rerun" = "red")) +
        theme(legend.position="none") +  geom_hline(yintercept=10, linetype="dashed", 
                color = "black", linewidth=1)  + 
              guides(fill=guide_legend(title="CV Between Dups <10%"))


SO4_dups1 <- ggplot(data =QAdups, aes(x =row_num, y =SO4_dups_diff, fill=SO4_dups_diff_flag)) +
       geom_bar(stat = 'identity') + 
        theme_classic() + labs(x= " ", y="Difference Between Sulfate Duplicates (%)") + 
        scale_fill_manual(values = c("YES" = "darkgreen", "No, rerun" = "red")) +
        theme(legend.position="none") +  geom_hline(yintercept=10, linetype="dashed", 
                color = "black", linewidth=1) + 
              guides(fill=guide_legend(title="CV Between Dups <10%"))

ggarrange(Cl_dups1, SO4_dups1,ncol=2, nrow=1)

#Zeros will create NAs in the flag column, so we need to switch those to Yes's 
QAdups <- QAdups %>%
  mutate(Cl_dups_diff_flag = if_else(is.na(Cl_dups_diff), "YES", Cl_dups_diff_flag)) %>%
  mutate(SO4_dups_diff_flag = if_else(is.na(SO4_dups_diff), "YES", SO4_dups_diff_flag))

#calculate the percent of dups that are within the range based on the flag 
cl_dups_diff_percent <- (sum(QAdups$Cl_dups_diff_flag == "YES")/nrow(QAdups))*100
so4_dups_diff_percent <- (sum(QAdups$SO4_dups_diff_flag == "YES")/nrow(QAdups))*100

#report out if the dups are within range
ifelse(cl_dups_diff_percent >= chks_flag, ">80% of Chloride Duplicates have a percent difference <10% - PROCEED",
       "<80% of Chloride Duplicates have a CV <10% - REASSESS")
ifelse(so4_dups_diff_percent >= chks_flag, ">80% of Sulfate Duplicates have a percent difference <10% - PROCEED",
       "<80% of Sulfate Duplicates have a CV <10% - REASSESS")

#write out a flag to the sample dataframe if more than 80% of the dups have percent differences out of range 
if (cl_dups_diff_percent <= chks_flag) {
    all_dat$Cl_QAQC_flag <- ifelse(
    all_dat$Cl_QAQC_flag != "",
    paste0(all_dat$Cl_QAQC_flag, "; Cl dups perc diff out of range"),
    "Cl dups out of range"
  )
}

if (so4_dups_diff_percent <= chks_flag) {  
    all_dat$SO4_QAQC_flag <- ifelse(
    all_dat$SO4_QAQC_flag != "",
    paste0(all_dat$SO4_QAQC_flag, "; SO4 dups perc diff out of range"),
    "SO4 dups out of range"
  )
}


```

## Calculate mmol/L concentrations & salinity, add dilutions
```{r Unit Conversion and Salinity Calculation, results = 'hide'}

# Convert ppm to mmol/L
all_dat$SO4_Conc_mM <- (all_dat$SO4_ppm / s_mw)
all_dat$Cl_Conc_mM <- (all_dat$Cl_ppm / cl_mw)

# Calculate Salinity 
# calculated using the Knudsen equation 
# Salinity = 0.03 + 1.8050 * Chlorinity
# Ref: A Practical Handbook of Seawater Analysis by Strickland & Parsons (P. 11)
# =((1.807*Cl_ppm)+0.026)/1000
all_dat$salinity <- ((1.8070 * all_dat$Cl_ppm) + 0.026) / 1000

```

## Check samples with metadata
```{r Check metadata, echo=FALSE}

#Check which samples from metadata were not ran because they had no water or were unfilitered 
all_present <- all(dionex_metadata$Cl_SO4_ID %in% all_dat$sample_ID )

if (all_present) {
  message("All sample IDs are present in metadata.")
} else {
  message("Some sample IDs are missing from metadata.")
  
  # Optional: Which ones are missing?
  missing_ids <- setdiff(dionex_metadata$Cl_SO4_ID, all_dat$sample_ID)
  print(missing_ids)
}

#merge dilution with sample run data 
merged_data <- all_dat %>%
  left_join(dionex_metadata, by = c("sample_ID" = "Cl_SO4_ID"))

```

## Add in dilution factors 
```{r add dilution factors, echo=FALSE}

#we will add in dilution factors based on the type of sample 
  #Upland wells are 50x, Wetland and water samples are 100x 

#make the new column then we will replace it based on the sample 
merged_data$Dilution <- 100  #majority of samples are a 100x dilution 

merged_data <- merged_data %>%
  mutate(Dilution = if_else(str_detect(sample_ID, "UP"), 50, Dilution)) %>%
  mutate(Dilution = if_else(str_detect(sample_ID, "Standard"), 1, Dilution)) %>%
  mutate(Dilution = if_else(str_detect(sample_ID, "Blank"), 1, Dilution)) 

```


## Assess Analytical Spikes
```{r Assess Spikes, echo=FALSE}

#pull out any rows that have "spk" in the Sample ID column
spks <- merged_data %>%  
  select(c(sample_ID, SO4_Conc_mM, SO4_ppm, Dilution)) %>%
  filter(str_detect(sample_ID, "spk"))      #have to change this to match data
# head(spks)

#create a new dataframe and remove dups from sample dataframe 
dat_spks <- merged_data %>%  
  filter(!str_detect(sample_ID, "spk")) %>%  
  select(c(sample_ID, SO4_Conc_mM, SO4_ppm))

#remove the dup from these IDs so we will have duplicate sample names
spks <- spks %>%
  mutate(sample_ID = gsub("_spk", "", as.character(sample_ID))) %>%
  rename(
    sample_ID = sample_ID,
    SO4_Conc_mM_spk = SO4_Conc_mM, 
    SO4_ppm_spk = SO4_ppm
  )

#put it back together with the old data set and look for duplicates 
QAspks <- merge(dat_spks, spks, by = "sample_ID")
# head(QAspks)

#spike for these samples was 10uL of the 250 µg/mL SO4 standard
QAspks$SO4_spk_Conc <- spk_Conc     # mmoles of SO4 in spike
# head(QAspks)

#Set Sample volumes in uL 
QAspks$SampleVol <- SampleVol

#change sample volume to L 
QAspks$SampleVol <- QAspks$SampleVol/Con1
# head(QAspks)

#gives us the total SO4 in the sample in mmoles
#mmol/L * L = mmol
#Want actual amount so divide by the dilution used by the Dionex to calculate the concentration 
QAspks$SO4_Total_unspkd <- (QAspks$SO4_Conc_mM/QAspks$Dilution)*(QAspks$SampleVol) 

#gives us the total SO4 in the spiked sample in mmoles
QAspks$SO4_Total_spkd <- (QAspks$SO4_Conc_mM_spk/QAspks$Dilution)*(QAspks$SampleVol+spkvol) 

#gives us expected SO4 in the spiked sample in mmoles
QAspks$SO4_expctd_spkd <-  (QAspks$SO4_Total_unspkd + QAspks$SO4_spk_Conc)

#gives us recovery of SO4 in the spiked sample in mmoles (actual/expected * 100)
QAspks$spk_recovery <-    (QAspks$SO4_Total_spkd/QAspks$SO4_expctd_spkd)*100

#flags if recovery of SO4 is outside range
QAspks$SO4_spks_flag <-  ifelse(QAspks$spk_recovery <= high_recovery_cutoff & QAspks$spk_recovery >= low_recovery_cutoff , 'Yes', 'No, rerun')

# head(QAspks)

#plot spk recoveries output as a bar graph to easily check - want any over 10% to be red need to work on this 
spksbar <- ggplot(data = QAspks, aes(x = sample_ID, y = spk_recovery, fill=SO4_spks_flag)) +
            geom_bar(stat = 'identity') + 
            theme_bw() + labs(x= "Sample ID", y="Spike Recovery (%)") + 
            geom_hline(yintercept=80, linetype="dashed", color = "black", linewidth=1) + 
            geom_hline(yintercept=120, linetype="dashed", color = "black", linewidth=1)+
            scale_fill_manual(values = c("Yes" = "darkgreen", "No, rerun" = "darkred"))+
            theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
            theme(legend.position="none")

spksbar


#check for percent of No, reruns to see if it  would warrant reruns 
Perc_spks <- QAspks %>% 
  group_by(SO4_spks_flag) %>%
  summarise(no_rows = length(SO4_spks_flag)) 
Perc_spks$Total <- length(QAspks$SO4_spks_flag)
Perc_spks$Percent <- (Perc_spks$no_rows / Perc_spks$Total)*100
# head(Perc_spks)

#select only the samples that passed the check
Perc_spks <- Perc_spks %>%
  filter(grepl("Yes", SO4_spks_flag))

#report out if the dups are within range
ifelse(Perc_spks$Percent >= chks_flag, ">80% of SO4 spikes have a recovery between the high and low cutoff - PROCEED",
       "<80% of SO4 spikes have a recovery between the high and low cutoff - REASSESS")

#write out a flag to the sample dataframe if less than 80% of the SO4 spikes are within range 
if (Perc_spks$Percent <= chks_flag) {
    all_dat$SO4_QAQC_flag <- ifelse(
    all_dat$SO4_QAQC_flag != "",
    paste0(all_dat$SO4_QAQC_flag, "; SO4 spikes out of range"),
    "SO4 spikes out of range"
  )
}

```


## Check if samples within the range of the standard curve
```{r Sample Flagging, echo=FALSE}

cat("Sample Flagging")

#Dilute samples 
merged_data$Cl_ppm_dil <- merged_data$Cl_ppm/merged_data$Dilution
merged_data$SO4_ppm_dil <- merged_data$SO4_ppm/merged_data$Dilution

#Remove standards
dat_flagged <- merged_data %>%  
            filter(!str_detect(sample_ID, "Standard")) %>%  
            filter(!str_detect(sample_ID, "Blank"))

#Flagging data if the concentration is outside the standards range and based on blanks
dat_flagged <- dat_flagged %>%
  mutate(
    Cl_Conc_flag = case_when(
      Cl_ppm_dil <= 0 ~ "bdl",
      Cl_ppm_dil > top_std_cl ~ "adl",
      Cl_ppm_dil > 0 & Cl_ppm_dil < top_std_cl ~ "Within_Range",
      TRUE ~ NA_character_  )) # fallback for unexpected values

dat_flagged <- dat_flagged %>%
  mutate(
    SO4_Conc_flag = case_when(
      SO4_ppm_dil <= 0 ~ "bdl",
      SO4_ppm_dil > top_std_so4 ~ "adl",
      SO4_ppm_dil > 0 & SO4_ppm_dil < top_std_so4 ~ "Within_Range",
      TRUE ~ NA_character_  )) # fallback for unexpected values


#Plot data and change colors based on flags to check it: 
cl_samples_flag <-  ggplot(data = dat_flagged, aes(x = sample_name, y = Cl_ppm_dil, fill=Cl_Conc_flag)) +
       geom_bar(stat = 'identity') + 
        scale_fill_manual(values = c("bdl" = "darkblue", "adl" = "red", "Within_Range" = "darkgreen")) +
        theme_classic() + labs(x= " ", y="Cl (diluted ppm)", title="Cl: Green = Within Range of Curve") + 
        theme(plot.title = element_text(size = 12)) +
        theme(legend.position = "bottom") +
        theme(axis.text.x = element_blank())

so4_samples_flag <-  ggplot(data = dat_flagged, aes(x = sample_name, y = SO4_ppm_dil, fill=SO4_Conc_flag)) +
       geom_bar(stat = 'identity') + 
        scale_fill_manual(values = c("bdl" = "darkblue", "adl" = "red", "Within_Range" = "darkgreen")) +
        theme_classic() + labs(x= " ", y="SO4 (diluted ppm)", title="SO4: Green = Within Range of Curve") + 
        theme(plot.title = element_text(size = 12)) + 
        theme(legend.position = "bottom") +
        theme(axis.text.x = element_blank())

ggarrange(cl_samples_flag, so4_samples_flag, nrow=1, ncol=2)

##Get number of samples bdl, adl, and within range
length = length(dat_flagged$SO4_Conc_flag) 
Perc_SO4_flagged <- dat_flagged %>% 
  group_by(SO4_Conc_flag) %>%
  summarise(Percent_samples = n()/length*100)

length = length(dat_flagged$Cl_Conc_flag) 
Perc_Cl_flagged <- dat_flagged %>% 
  group_by(Cl_Conc_flag) %>%
  summarise(Percent_samples = n()/length*100)


knitr::kable(Perc_SO4_flagged, caption = "SO4 samples")
knitr::kable(Perc_Cl_flagged, caption = "Cl samples")

```


\newpage

## Visualize Data
```{r Visualize Data, echo=FALSE}
cat("Visualize Data")

#Plot samples to get a first look at concentrations (sanity check)
IDs <- data.frame(do.call('rbind', strsplit(as.character(dat_flagged$sample_ID),'_',fixed=TRUE)))
colnames(IDs) <- c("Experiment" , "Site_Code","Sample_Type", "Time_Point", "Extra1", "Extra2")
#head(IDs)

#remove any lines that do not have TOC/TN data in dat_flagged
#dat_flagged <- dat_flagged %>%
 # na.omit()

#rejoin them to the dataframe
dat_flagged_id <- cbind(IDs, dat_flagged)

#create important columns from the sample_name 
dat_flagged_id <- dat_flagged_id %>%
  mutate(date_sampled = as.character(date_sampled)) %>%
  mutate(
    Sample_Type = if_else(
      str_detect(sample_ID, regex("T\\d+", ignore_case = TRUE)),
      "SW",
      "Endmember"),
    Sample_Date = if_else(
      str_detect(date_sampled, "^\\d+$"),  # string contains only digits from start to end str_remove("\\d{8}")
      date_sampled,
      NA_character_ ),
    Time = if_else(
      str_detect(time_sampled_est, "^\\d+$"),  # string contains only digits from start to end
      time_sampled_est,
      NA_character_ ), 
    Paired = if_else(
      str_detect(sample_ID, "Pair"),
      "Paired",
      NA_character_)) %>%
  filter(!str_detect(sample_ID, regex("_dup", ignore_case = TRUE))) #remove duplicates  

#Plot data and change colors based on flags to check it: 
viz_cl_plot <- ggplot(dat_flagged_id, aes(x = sample_ID, y = Cl_ppm, fill = Sample_Type)) +
  geom_bar(stat = "identity", position = position_dodge2(preserve = "single")) +
  theme_classic() +
  labs(x = " ", y = "Chloride (mg/L)", title = "Samples: Cl") +
  theme(legend.position = "right") + theme(legend.position="right")  + 
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5))


viz_so4_plot <-  ggplot(dat_flagged_id, aes(x = sample_ID, y = SO4_ppm, fill = Sample_Type)) +
  geom_bar(stat = "identity", position = position_dodge2(preserve = "single")) +
  theme_classic() +
  labs(x = " ", y = "Sulfate (mg/L)", title = "Samples: SO4")  +
  theme(legend.position = "right") + theme(legend.position="right")  + 
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5))

viz_cl_plot
viz_so4_plot

#ggarrange(viz_c_plot, viz_n_plot, nrow=2, ncol=1)
```


## Export Processed Data  
```{r Export Processed Data, echo=FALSE, include = FALSE}

#Prepare data to be exported - if there is anything else to add 
#Add any necessary identifiers to the samples  ### VERY IMPORTANT AND STANDARD FOR PROJECT ####
  #example read in sample IDs list and merge 
  #create required ID columns in R, etc. 
final_data <- dat_flagged_id %>% 
  mutate(
    Project = "COMPASS: Synoptic",   # new column with same value on every row
    Region = "CB",
    Run_notes = run_notes,
    Analysis_runtime = print(Date_Run)
  ) 


final_data <- final_data %>%
    rename(Sample_ID = sample_ID) %>%
  select(Project, Region, Experiment, Site_Code, Sample_Type, Sample_ID, 
         Sample_Date, Time, Paired, sample_name,
         SO4_Conc_mM, SO4_Conc_flag, SO4_QAQC_flag, Cl_Conc_mM, Cl_Conc_flag, Cl_QAQC_flag, salinity,
         Analysis_runtime, Run_notes,  
    # list columns in the order you want them
  )

head(final_data)

#will put final data in processed data folder 
#Write out data frame 
  write.csv(final_data, processed_file_name)

```


#end