---
title: "SLP Flow Adjustments"
author: "Stephanie J. Wilson"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = "allow")
```

```{r packages, warning=FALSE, include=FALSE}
library(tidyverse)
library(lubridate)
library(ModelMetrics)
library(rmarkdown)
library(Tides)
library(pracma)
library(zoo)
```

```{r read data, include=FALSE}
rm(list=ls())
sensor_data <- read.csv("derived-data/sensor_data.csv")
  #GEPsy <- read.csv("../../Data/Original/SLP_USGS_WHOI/WBsy2.csv")
if("X" %in% colnames(sensor_data))
{sensor_data=select(sensor_data, -X)}
if("tide_num" %in% colnames(sensor_data))
{sensor_data=select(sensor_data, -tide_num)}
source("flux_processing_functions.R")
```

## Overland Flow Corrections

# We don't have a quadratic overland flow correction for SERC 
# linear overland flood correction - we are skipping for now
H>5

```{#r Overland flow}
sensor_data <- mutate(sensor_data, 
                      flow_land = if_else(H>0.5, (H*9.170833-1.320587)*flow, flow))

  #where do the numbers here come from? The 9.170833 and 1.32058??
      #these numbers are specific to the DEM model for their site and the waterdrop analysis

#maybe worth asking Emily - Qipei will talk to Emily and then report back to me with 
  #a protocol for figuring out how the waterdrop and DEM data can be used to do it for GCReW 
  #for now we will assume no overland flow 

#ggplot(data=sensor_data, aes(x=datetime, y=H)) + geom_point()


#we might be able to use NAVD88 creek edge measurements 
  #we would need to make sure that the exo data is also NAVD88 reffed 
  
#can just take a estimate of double what is reasonable for now. 

```

## Assigning tide numbers

```{r add concentration to sensor data, warning=FALSE}
#dataframe for Tide package
sensor_data<-sensor_data%>%
  mutate(datetime=ymd_hms(datetime, truncated = 3))

h<-tibble(time=sensor_data$datetime, h=sensor_data$H)
h<-na.omit(h)
datetime2<-h$time #used in Line 67
h0<-mean(sensor_data$H, na.rm=TRUE)
tidal_dat <- TidalCharacteristics(h=h, h0 = h0, 
                          T2 = 5 * 60 * 60, hoffset = 0,
                          filtconst = 1, dtMax = 30, unit = "mins", 
                          Tavg = 12 * 60, removegaps = "All")
#extract result
HL<-tidal_dat$h$HL
halftide_num<-tidal_dat$h$N
tide_num<-idivide(halftide_num, 2, "round")
tidal_dat_sub<-tibble(datetime=datetime2, HL, halftide_num, tide_num)
sensor_data<-left_join(sensor_data,tidal_dat_sub,by="datetime")
```

## Remove tides with severely unbalanced water budgets

The cutoff value is 5000 m$^3$ per tide. Tides with unbalanced water budgets
greater than 5000 m$^3$ per tide won't be considered for further analysis.

Compared to previously used 1000, I relax the threshold.

```{r check water budgets, warning=FALSE, message=FALSE}
water_check <- sensor_data%>%
  group_by(tide_num)%>%#300s=5min
  summarise(flow_tide_sum=sum(flow_land)*300)%>%
  filter(abs(flow_tide_sum)>5000)
rm_inst <- which(sensor_data$tide_num %in% water_check$tide_num)
sensor_data$flow_land[rm_inst]<-NA
print("how many tides are removed?")
nrow(water_check)
rm(rm_inst)

#TA check
TA_check<-sensor_data%>%
  select(tide_num,flow_land,TA)%>%
  mutate(flux=TA*flow_land)%>%
  group_by(tide_num)%>%
  summarize(N=length(na.omit(flux)),
            N_t=length(na.omit(tide_num)))%>%
  mutate(A.pct=N/N_t*100)%>%
  filter(A.pct>80) #note here, the threshold is relaxed

sensor_data$flow_land[which(!(sensor_data$tide_num %in% TA_check$tide_num))]<-NA
#sensor_data$TA[which(!(sensor_data$tide_num %in% TA_check$tide_num))]<-NA

water_check2 <- sensor_data%>%
  group_by(tide_num)%>%#300s=5min
  summarise(flow_tide_sum=sum(flow_land)*300)

p_water_check2<-ggplot(water_check2, aes(x=flow_tide_sum)) + 
  geom_histogram(color="black", fill="white") +
  labs(x = expression(paste("Tidal water budgets"," (m"^3,")")))
  
p_water_check2
```

## Flow adjustments based on the salt budget

```{r salt budgets, error=FALSE, message=FALSE}
#To determine groundwater inputs based on salt balance. 
#Adjustments only apply to ebb flows.
sensor_data$flow_corr <- sensor_data$flow_land
sensor_data$month <- month(sensor_data$datetime)
sensor_data$year <- year(sensor_data$datetime)
sensor_data$season <- month2season(sensor_data$month)

#shift_corr is a factor applied to ebb tides
m_list <- group_by_at(sensor_data, c("year","month"))%>%summarize()
m_list <- na.omit(m_list)
shift_corr <- rep(NA,nrow(m_list))

#create a 'for' loop to process every season each year
for(i in 1:length(shift_corr)){
  M <- m_list$month[i]
  Y <- m_list$year[i]
  month <- filter(sensor_data, month == M, year == Y)
  water_budget <- filter(GEPsy, year == Y, season == month2season(M))
  #determine shift_corr
  ebb_mean <- mean(month$flow_land[which(month$flow_land<0)],na.rm=TRUE)
  flood_mean <- mean(month$flow_land[which(month$flow_land>0)],na.rm=TRUE)
  tot_mean <- mean(month$flow_land,na.rm=TRUE)
  ebb_n <- length(which(month$flow_land<0))
  flood_n <- length(which(month$flow_land>0))
  tot_n <- ebb_n+flood_n
  shift_corr[i] <- (water_budget$salt_bal_m3s-(flood_n*flood_mean)/tot_n)*
    (tot_n/(ebb_n*ebb_mean))
  #
  ebbs <- which(sensor_data$flow_land<0 & sensor_data$month == M & sensor_data$year == Y)
  sensor_data$flow_corr[ebbs] <- sensor_data$flow_land[ebbs]*shift_corr[i]
}
```

```{r save data}
write.csv(sensor_data, "../../Data/Derivative/SLP_USGS_WHOI/sensor_data.csv",
          row.names = FALSE)
```