---
title: "bottle-data-model-trials"
author: "Stephanie J. Wilson"
date: "2025-05-28"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = "allow")
```

```{r packages, warning=FALSE,include=FALSE}
library(tidyverse)
library(lubridate)
library(ModelMetrics)
library(rmarkdown)
```

```{r read data,include=FALSE}
rm(list=ls())
DIC_bottle_data <- read.csv("derived-data/DIC_bottle_data.csv")
DOC_bottle_data <- read.csv("derived-data/DOC_bottle_data.csv")
sensor_data <- read.csv("derived-data/sensor_data.csv")
if("DIC" %in% colnames(sensor_data))
{sensor_data=select(sensor_data, -DIC, -DOC)}
```

## DIC plots - look for a situtation where we may have cutoffs to increase R2 values

  #try - set a cut off variable on the DIC and consider it 
  #try to figure out what the high DIC values are and if they are related to something specific 
    #if there is a mechanistic explanation of the 
  #if the multiple linear regression doesn't work we can try machine learning 
  
```{r plot DIC data and look for vars that are important}

DIC1 <- ggplot(data=DIC_bottle_data, aes(x=pH, y=DIC)) + 
  geom_point(size=3, col="blue")  + theme_classic()
DIC1


DIC2 <- ggplot(data=DIC_bottle_data, aes(x=pH, y=DIC)) + 
  geom_point(size=3, col="purple")  + theme_classic()
DIC2

DIC3 <- ggplot(data=DIC_bottle_data, aes(x=S, y=DIC)) + 
  geom_point(size=3, col="red")  + theme_classic()
DIC3

DIC4 <- ggplot(data=DIC_bottle_data, aes(x=DO, y=DIC)) + 
  geom_point(size=3, col="darkgreen")  + theme_classic()
DIC4

DIC5 <- ggplot(data=DIC_bottle_data, aes(x=flow, y=DIC)) + 
  geom_point(size=3)  + theme_classic()
DIC5

```

## DIC model

```{r fit DIC model}
DIC_model <- lm(log10(DIC) ~ log10(pH) + log10(T) + log10(S) + log10(DO) , 
                data = DIC_bottle_data, na.action=na.omit)

summary(DIC_model)
print('DIC model RMSE')
rmse(10^DIC_model$fitted.values, DIC_bottle_data$DIC)
```

## DOC plot

```{r plot DOC data and look for vars that are important}

DOC1 <- ggplot(data=DOC_bottle_data, aes(x=H, y=DOC)) + 
  geom_point(size=3, col="blue")  + theme_classic()
DOC1


DOC2 <- ggplot(data=DOC_bottle_data, aes(x=pH, y=DOC)) + 
  geom_point(size=3, col="purple")  + theme_classic()
DOC2

DOC3 <- ggplot(data=DOC_bottle_data, aes(x=S, y=DOC)) + 
  geom_point(size=3, col="red")  + theme_classic()
DOC3

DOC4 <- ggplot(data=DOC_bottle_data, aes(x=DO, y=DOC)) + 
  geom_point(size=3, col="darkgreen")  + theme_classic()
DOC4

DOC5 <- ggplot(data=DOC_bottle_data, aes(x=flow, y=DOC)) + 
  geom_point(size=3)  + theme_classic()
DOC5

```


## DOC model

fDOM improves the model performance, yet with a lower data coverage.

The two model versions (a and b) differs by whether fDOM will be used.

```{r fit DOC model, echo=TRUE}
#version a
DOC_bottle_data_fDOM <- filter(DOC_bottle_data, fDOM > 0)
DOC_modela <- lm(log10(DOC) ~ log10(pH) + log10(T) + log(fDOM), 
                 data = DOC_bottle_data_fDOM)
summary(DOC_modela)
print('DOC modela RMSE')
rmse(10^DOC_modela$fitted.values, DOC_bottle_data_fDOM$DOC)

#version b
DOC_modelb <- lm(log10(DOC) ~ log10(pH) + log10(T), 
                 data = DOC_bottle_data, na.action=na.omit)
summary(DOC_modelb)
print('DOC modelb RMSE')
rmse(10^DOC_modelb$fitted.values, DOC_bottle_data$DOC)
```

